---
pagetitle: "`r paste0('Capacity - ', country)`"
title-block: false
---

```{r cap-level2-headings}
# placeholder for sourcing level 2 headings

```

::: {.grid .align-items-center}
:::: {.g-col-9}
[Capacity - {{< var doc.country >}}]{.fakeh1}
::::

:::: {.g-col-3}
<span class="no-external-icon">[<i class="fa fa-download"></i> Download Report](`r params$home_address`/download/{{< var doc.year_report >}}/PRB-Annual-Monitoring-Report_{{< var doc.country >}}_{{< var doc.year_report >}}.pdf){.btn .btn-light .text-dark .border .bg-secondary-subtle .rounded}</span>
::::
:::

## PRB monitoring

```{r cap-prb}
if (params$country == "Luxembourg") {
  cap_er_conc1 <- ""
  } else {
  cap_er_conc1 <- get_prb_conclusions(prb_findings_file, "ER_capacity", "Table_Findings_ER_capacity")
}
```

`r cap_er_conc1`

`r if (params$no_tcz == 0) ":::: {.content-hidden}"`

```{r cap-trm-prb}
cap_trm_conc1 <- get_prb_conclusions(prb_findings_file, "TRM_capacity", "Table_Findings_TRM_capacity")

cap_trm_conc1 <- if_else(cap_trm_conc1 == "NA" | stringr::str_detect(cap_trm_conc1, "character"), "", cap_trm_conc1)
```

`r cap_trm_conc1`

`r if (params$no_tcz == 0) "::::"`


`r if (params$country == "Luxembourg") "::: {.content-hidden}"`
::: {#container-cap-er}
## En route performance

### [**En route ATFM delay**](`r params$home_address`/about.html#capacity---average-en-route-atfm-delay-per-flight-kpi1) (KPI#1)

:::: {layout="[ 50, 50 ]"}
::::: {.chart-container}  
```{r chart_cap_er, options = (cztype=c("enroute"))}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```
:::::

::::: {.chart-container}  
```{r chart_cap_er_month, options = (cztype=c("enroute"))}
#| file: R/chart_level2_cap_month.R
#| out.width: "100%"
```
:::::
::::

`r if (country == "MUAC" | country == "FABEC") ":::: {.content-hidden}"`
:::: {layout="[ 20, 60, 20 ]"}

::::: {#empty-div}
:::::

::::: {.chart-container}  
```{r chart_level2_cap_delay_bin}
#| file: R/chart_level2_cap_delay_bin.R
#| out.width: "100%"
```
:::::

::::: {#empty-div}
:::::

::::

`r if (country == "MUAC" | country == "FABEC") "::::"`

:::


`r if (params$country == params$rp_full | params$country == "MUAC") "::: {.content-hidden}"`
::: {.callout-note collapse=true}

#### Focus on en route ATFM delay

**En route ATFM delay**

```{r cap_er_text_atfm, eval=((params$no_ecz != 0) | (params$country == "FABEC")) }
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_er_atfm.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

cat("\n\n")

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_cap_er_atfm.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, cap_er_nsa_titles_atfm)

``` 

`r if (params$country == "FABEC") ":::: {.content-hidden}"`

**En route capacity incentive scheme**

```{r cap_er_text_incentive, eval=(params$no_ecz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_er_incentive.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

`r if (params$country == "FABEC") "::::"`

:::
`r if (params$country == params$rp_full | params$country == "MUAC") ":::"`

`r if (params$country == params$rp_full | params$country == "FABEC") "::: {.content-hidden}"`

### [**En route performance indicators at ACC level (PI#4-5)**](`r params$home_address`/about.html#capacity---to-be-added)

:::: {layout="[ 50, 50 ]"}
::::: {.chart-container}  
```{r chart_level2_cap_perc_delay_above}
#| file: R/chart_level2_cap_perc_delay_above.R
#| out.width: "100%"
```
:::::

::::: {.chart-container}  
```{r chart_level2_cap_peak_tp}
#| file: R/chart_level2_cap_peak_tp.R
#| out.width: "100%"
```
:::::
::::

:::: {.callout-note collapse=true}


#### Focus en route performance indicators at ACC level

**Percentage of total en route ATFM delay that occurred on days when the daily throughput was above the expected daily traffic**

```{r cap_ert_text_above}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_er_above.qmd", as.character(year_report),country,country, as.character(year_report))

mytext1 <- replace_headings(path, character(0))
cat(mytext1)

cat("\n\n")

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_cap_er_above.qmd", as.character(year_report),country,country, as.character(year_report))

mytext2 <- replace_headings(path, cap_er_nsa_titles_above)
if(is.null(mytext1) & is.null(mytext2)){cat("No comment provided.")} else {cat(mytext2)}
``` 

**Annual weighted average of the daily peak throughput**

```{r cap_ert_text_tput}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_er_tput.qmd", as.character(year_report),country,country, as.character(year_report))

mytext1 <- replace_headings(path, character(0))
cat(mytext1)

cat("\n\n")

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_cap_er_tput.qmd", as.character(year_report),country,country, as.character(year_report))

mytext2 <- replace_headings(path, cap_er_nsa_titles_tput)
if(is.null(mytext1) & is.null(mytext2)){cat("No comment provided.")} else {cat(mytext2)}
``` 

::::

`r if (params$country == params$rp_full | params$country == "FABEC") ":::"`


`r if (params$country != params$rp_full) "::: {.content-hidden}"`
### Summary of performance at local level

:::: {layout="[ 20, 60, 20 ]"}

::::: {#empty-div}
:::::

::::: {.chart-container}  
```{r table_erdelay_summary}
#| file: R/table_cap_erdelay_all_states.R
#| out.width: "100%"
```
:::::

::::: {#empty-div}
:::::

::::

`r if (params$country != params$rp_full) ":::"`


`r if (params$country == "FABEC") "::: {.content-hidden}"`

::: {#container-cap-atco}

### [**Other indicators**](`r params$home_address`/about.html#capacity-oher-en-route-indicators)

:::: {layout="[ 50, 50 ]"}

::::: {.chart-container}  
```{r chart_cap_atco}
#| file: R/chart_level2_cap_atco.R
#| out.width: "100%"
```
:::::

::::: {.chart-container}  
<!-- for ses there is no graphic per acc -->
`r if (params$country == params$rp_full) ":::::: {.content-hidden}"`
```{r chart_cap_atco_acc}
#| file: R/chart_level2_cap_atco_acc.R
#| out.width: "100%"
```
`r if (params$country == params$rp_full) "::::::"`

<!-- so we replace it by thee sector opening hours -->
`r if (params$country != params$rp_full) ":::::: {.content-hidden}"`
```{r chart_cap-sector_opening_ses}
#| file: R/chart_level2_cap_sector_opening.R
#| out.width: "100%"
```
`r if (params$country != params$rp_full) "::::::"`
:::::
::::

<!-- for ses this chart is now above, so we hide it here -->
`r if (params$country == params$rp_full) ":::: {.content-hidden}"`

:::: {layout="[ 20, 60, 20 ]"}

::::: {#empty-div}
:::::

::::: {.chart-container}  
```{r chart_cap_sector_opening}
#| file: R/chart_level2_cap_sector_opening.R
#| out.width: "100%"
```
:::::
::::
`r if (params$country == params$rp_full) "::::"`

:::

`r if (params$country == params$rp_full) "::: {.content-hidden}"`
::: {.callout-note collapse=true}

#### Focus on ATCOs in operations

:::: {#concl-cap-atco}

**ATCOs in operations**

```{r cap_ert_text_atco}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_er_atco.qmd", as.character(year_report),country,country, as.character(year_report))

mytext1 <- replace_headings(path, character(0))
cat(mytext1)

cat("\n\n")

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_cap_er_atco.qmd", as.character(year_report),country,country, as.character(year_report))

mytext2 <- replace_headings(path, cap_er_nsa_titles_atco)
if(is.null(mytext1) & is.null(mytext2)){cat("No comment provided.")} else {cat(mytext2)}
``` 

::::
:::
`r if (params$country == params$rp_full) ":::"`

`r if (params$country == "FABEC") ":::"`

`r if (params$country == "Luxembourg") ":::"`


`r if (params$no_tcz == 0) "::: {.content-hidden}"`

:::: {#container-cap-trm}
## Terminal performance

### [**Arrival ATFM delay**](`r params$home_address`/about.html#capacity---average-en-route-atfm-delay-per-flight-kpi1) (KPI#2)

::::: {layout="[ 50, 50 ]"}

:::::: {.chart-container}  
```{r chart_cap_trm, options = (cztype=c("terminal"))}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```
::::::

:::::: {.chart-container}  
```{r chart_cap_trm_month, options = (cztype=c("terminal"))}
#| file: R/chart_level2_cap_month.R
#| out.width: "100%"
```
::::::
:::::

::::


`r if (params$country != params$rp_full) ":::: {.content-hidden}"`
### Summary of performance at local level

:::: {layout="[ 20, 60, 20 ]"}

::::: {#empty-div}
:::::

::::: {.chart-container}  
```{r table_arrdelay_summary}
#| file: R/table_cap_arrdelay_all_states.R
#| out.width: "100%"
```
:::::

::::: {#empty-div}
:::::

::::

`r if (params$country != params$rp_full) "::::"`


`r if (params$country == params$rp_full) ":::: {.content-hidden}"`
:::: {.callout-note collapse=true}

#### Focus on arrival ATFM delay

::::: {#concl-cap-trm}

**Arrival ATFM delay**

```{r cap_trm_text_atfm, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_trm_atfm.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

cat("\n\n")

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_cap_trm_atfm.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, cap_trm_nsa_titles_atfm)

``` 

**Terminal capacity incentive scheme**

```{r cap_trm_text_incentive, eval=(params$no_ecz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_trm_incentive.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

:::::
::::


:::: {#container-cap-other}

### [**Other terminal performance indicators**](`r params$home_address`/about.html#capacity---other-terminal-performance-indicators-pi1-3) (PI#1-3)

::::: {layout="[ 20, 60, 20 ]"}

:::::: {#empty-div}
::::::

:::::: {.chart-container}  
```{r chart_level2_cap_all_causes_delay}
#| file: R/chart_level2_cap_all_causes_delay.R
#| out.width: "100%"
```
::::::
:::::

::::

:::: {#container-cap-table-apt-pis}
```{r table-cap-apt-pis, eval=!(params$no_tcz == 0 | params$country == params$rp_full)}
#| file: R/table_level2_cap_apt_pis.R
#| out.width: "100%"
```
::::

:::: {.callout-note collapse=true}

#### Focus on performance indicators at airport level
::::: {#concl-cap-apt-pis}

**ATFM slot adherence**

```{r cap_trm_text_slot, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_trm_slot.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

cat("\n\n")

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_cap_trm_slot.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, cap_trm_nsa_titles_slot)

``` 

**ATC pre-departure delay**

```{r cap_trm_text_pddelay, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_trm_pddelay.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_cap_trm_pddelay.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, cap_trm_nsa_titles_pddelay)

``` 

**All causes pre-departure delay**

```{r cap_trm_text_acdelay, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_trm_acdelay.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_cap_trm_acdelay.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, cap_trm_nsa_titles_acdelay)

``` 


:::::
::::
`r if (params$country == params$rp_full) "::::"`

`r if (params$no_tcz == 0) ":::"`


<!-- we need this graph for ses -->
`r if (params$country != params$rp_full) "::: {.content-hidden}"`

:::: {#container-cap-other-ses}
### Other performance indicators 

::::: {layout="[ 20, 60, 20 ]"}

:::::: {#empty-div}
::::::

:::::: {.chart-container}  
```{r chart_cap_all_causes_delay_ses}
#| file: R/chart_level2_cap_all_causes_delay.R
#| out.width: "100%"
```
::::::
:::::

::::
`r if (params$country != params$rp_full) ":::"`
