```{r cef-level2-text}
cz=c("@@cz_index@@", "@@cz_type@@")
  
# define cz
czindex <- as.numeric(cz[[1]])
cztype <- cz[[2]]

if (cztype == "enroute") {
  cztype_proper <- "En route"
  no_cz <- params$no_ecz
  czname <- ecz_list$ecz_name[[czindex]]
  cz_short <- 'er'
  
} else {
  cztype_proper <- "Terminal"
  no_cz <- params$no_tcz
  czname <- tcz_list$tcz_name[[czindex]]
  cz_short <- 'tz'
}

cz=c("@@cz_index@@", "@@cz_type@@")
  
source("R/get_level2_headings.R")

```
::: {.grid .align-items-center}
:::: {.g-col-9}
[Cost-efficiency - {{< var doc.country >}}]{.fakeh1}
::::

:::: {.g-col-3}
<span class="no-external-icon">[<i class="fa fa-download"></i> Download Report](`r params$home_address`/download/{{< var doc.year_report >}}/PRB-Annual-Monitoring-Report_{{< var doc.country >}}_{{< var doc.year_report >}}.pdf){.btn .btn-light .text-dark .border .bg-secondary-subtle .rounded}</span>
::::
:::


`r if (cztype == 'terminal' | czindex == 2) "::: {.content-hidden}"`

## PRB monitoring

```{r concl-cef-duc}
cef_conc1 <- get_prb_conclusions(prb_findings_file, "cost-efficiency", "Table_Findings_CEFF")
```

`r cef_conc1`

`r if (cztype == 'terminal' | czindex == 2) ":::"`


`r if ((params$no_ecz == 1 & cztype == 'enroute') | (params$no_tcz == 1 & cztype == 'terminal')) "::: {.content-hidden}"`
## @@cz_type_proper@@ charging zone - {{< var doc.@@cz_short@@@@cz_index@@ >}}
`r if ((params$no_ecz == 1 & cztype == 'enroute') | (params$no_tcz == 1 & cztype == 'terminal')) ":::"`


`r if ((params$no_ecz != 1 & cztype == 'enroute') | (params$no_tcz >= 2 & cztype == 'terminal')) "::: {.content-hidden}"`
## @@cz_type_proper@@ charging zone
`r if ((params$no_ecz != 1 & cztype == 'enroute') | (params$no_tcz >= 2 & cztype == 'terminal')) ":::"`

::: {#container-cef-duc}

### [**Unit cost**](`r params$home_address`/about.html#cost-efficiency---unit-costs-ducaucu-kpi1) (KPI#1)

:::: {layout="[ 50, 50 ]"}

::::: {.chart-container}  
`r if (params$country == params$rp_full & cztype == "enroute") ":::::: {.content-hidden}"`
```{r chart_cef_duc, options = (cz=c("@@cz_index@@", "@@cz_type@@","level2"))}
#| file: R/chart_level1_cef.R
#| out.width: "100%"
```
`r if (params$country == params$rp_full & cztype == "enroute") "::::::"`

`r if (params$country != params$rp_full | cztype == "terminal") ":::::: {.content-hidden}"`
```{r chart_cef_duc_er_ses, options = (cz=c("@@cz_index@@", "@@cz_type@@")), eval=(params$country == params$rp_full)}
#| file: R/chart_level1_cef_er_ses.R
#| out.width: "100%"
```
`r if (params$country != params$rp_full | cztype == "terminal") "::::::"`

:::::

::::: {.chart-container}  
```{r chart_cef_su, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_su.R
#| out.width: "100%"
```
:::::
::::

:::: {layout="[ 50, 50 ]"}
::::: {.chart-container}  
```{r chart_cef_cost, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_cost.R
#| out.width: "100%"
```
:::::

::::: {#table-costs}
```{r table-cef-cost, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/table_level2_cef_cost.R
#| out.width: "100%"
```

`r if (params$country == params$rp_full) ":::::: {.content-hidden}"`

```{r table-cef-cost-infl, eval = (params$country != params$rp_full), options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/table_level2_cef_cost_infl.R
#| out.width: "100%"
```
`r if (params$country == params$rp_full) "::::::"`
:::::
::::


:::: {layout="[ 50, 50 ]"}
::::: {.chart-container}  
```{r chart_cef_cost_entity, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_cost_entity.R
#| out.width: "100%"
```
:::::

::::: {.chart-container}  
```{r chart_cef_cost_main, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_cost_main.R
#| out.width: "100%"
```
:::::
::::
:::


`r if (params$country != params$rp_full) "::: {.content-hidden}"`
### Summary of performance at local level

:::: {#table-cef-summary}
```{r table-cef-summary, options = (cztype="@@cz_type@@"), eval=params$country == params$rp_full}
#| file: R/table_cef_summary.R
#| out.width: "100%"
```
::::

`r if (params$country != params$rp_full) ":::"`


`r if (params$country == params$rp_full) "::: {.content-hidden}"`

::: {.callout-note collapse=true}

#### Focus on unit cost

```{r}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s_cef_%s%d_1.qmd", tolower(country), cz_short, czindex)

replace_headings(path, cef_titles_s1)

# if (file.exists(path)) {cat(sprintf("{{< include %s >}}", path))}
``` 

:::

`r if (params$country == params$rp_full) ":::"`


::: {#container-cef-aucu}

### Actual unit cost incurred by the users ([**AUCU**](`r params$home_address`/about.html#cost-efficiency---actual-unit-cost-incurred-by-the-users-aucu-pi1)) (PI#1)

:::: {layout="[ 50, 50 ]"}
::::: {.chart-container}  
```{r chart_cef_aucu, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_aucu.R
#| out.width: "100%"
```
:::::

::::: {#table-cef-aucu}
```{r table_cef_aucu, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/table_level2_cef_aucu.R
#| out.width: "100%"
```
:::::
::::


:::: {layout="[ 50, 50 ]"}
::::: {.chart-container}  
```{r chart_cef_cex, R.options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_cex.R
#| out.width: "100%"
```
:::::

::::: {#table_cef_er_cex}
```{r table_cef_cex, R.options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/table_level2_cef_cex_tbv.R
#| out.width: "100%"
```
:::::
::::
:::

`r if (params$country == params$rp_full) "::: {.content-hidden}"`

::: {.callout-note collapse=true}

#### Focus on AUCU

```{r}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s_cef_%s%d_2.qmd", tolower(country), cz_short, czindex)

replace_headings(path, cef_titles_s2)

``` 

:::

`r if (params$country == params$rp_full) ":::"`


::: {#container-cef-reg-res}

### Regulatory result ([**RR**](`r params$home_address`/about.html#cost-efficiency---regulatory-result-rr))

:::: {layout="[ 50, 50 ]"}
::::: {.chart-container}  
```{r chart_cef_reg_res, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_reg_res.R
#| out.width: "100%"
```
:::::

::::: {.chart-container}  
```{r chart_cef_reg_res_aucu,  options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_reg_res_aucu.R
#| out.width: "100%"
```
:::::
::::

:::: {layout="[ 50, 50 ]"}
::::: {.chart-container}  
```{r chart_cef_reg_res_ansp, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_reg_res_ansp.R
#| out.width: "100%"
```
:::::

::::: {.chart-container}  
```{r chart_cef_net_res_main_ansp, options = (cz=c("@@cz_index@@", "@@cz_type@@"))}
#| file: R/chart_level2_cef_net_res_main_ansp.R
#| out.width: "100%"
```
:::::
::::

:::

`r if (params$country == params$rp_full) "::: {.content-hidden}"`

::: {.callout-note collapse=true}

#### Focus on regulatory result

```{r}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s_cef_%s%d_3.qmd", tolower(country), cz_short, czindex)

replace_headings(path, cef_titles_s3)

```

:::

`r if (params$country == params$rp_full) ":::"`

