```{r cz_def_@@cz_type@@@@cz_index@@}
cz=c("@@cz_index@@", "@@cz_type@@")
  
# define cz
czindex <- as.numeric(cz[[1]])
cztype <- cz[[2]]

if (cztype == "enroute") {
  cztype_proper <- "En route"
  no_cz <- params$no_ecz
  czname <- ecz_list$ecz_name[[czindex]]
  
} else {
  cztype_proper <- "Terminal"
  no_cz <- params$no_tcz
  czname <- tcz_list$tcz_name[[czindex]]
}

```

```{r chart_cef_duc_l2_@@cz_type@@@@cz_index@@, options = (cz=c(czindex, cztype,"level2")), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level1_cef.R
#| out.width: "100%"
```

```{r chart_cef_su_l2_@@cz_type@@@@cz_index@@, options = (cz=c(czindex, cztype)), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level2_cef_su.R
#| out.width: "100%"
```



```{r chart_cef_cost_entity_@@cz_type@@@@cz_index@@, options = (cz=c(czindex, cztype)), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level2_cef_cost_entity.R
#| out.width: "100%"
```

```{r chart_cef_cost_main_@@cz_type@@@@cz_index@@, options = (cz=c(czindex, cztype)), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level2_cef_cost_main.R
#| out.width: "100%"
```

<!-- #### Actual unit cost incurred by the users (AUCU) (PI#1) -->

<!-- #### Regulatory result (RR) -->

```{r chart_cef_reg_res_@@cz_type@@@@cz_index@@, options = (cz=c(czindex, cztype)), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level2_cef_reg_res.R
#| out.width: "100%"
```

```{r chart_cef_reg_res_aucu_@@cz_type@@@@cz_index@@, options = (cz=c(czindex, cztype)), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level2_cef_reg_res_aucu.R
#| out.width: "100%"
```

```{r chart_cef_reg_res_ansp_@@cz_type@@@@cz_index@@, options = (cz=c(czindex, cztype)), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level2_cef_reg_res_ansp.R
#| out.width: "100%"
```

```{r chart_cef_net_res_main_ansp_@@cz_type@@@@cz_index@@, options = (cz=c(czindex, cztype)), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level2_cef_net_res_main_ansp.R
#| out.width: "100%"
```


```{r cef-level2-text-@@cz_type@@@@cz_index@@}
# if (czindex > no_ecz) {
# # do nothing
# 
# } else {
# 
# czname <- ecz_list$ecz_name[[czindex]]
# cef_level2_text <- get_cef_level2_text(czindex, cztype)
# }

  cef_txt_1_4_duc <- ''
  cef_txt_1_4_su <- '' 
  cef_txt_1_4_cost_all <- ''
  cef_txt_1_4_cost_main <- ''
  cef_txt_1_4 <- data.frame(a=c(NA,NA), b=c(NA,NA)) |> as_tibble()
  
  my_index_su <- 1
  my_index_cost_by_ent <- 1
  my_index_cost_main <- 1
  
  cef_txt_1_9 <- data.frame(a=c(NA,NA), b=c(NA,NA)) |> as_tibble()
  cef_txt_1_10_txt <- ''
  cef_txt_1_13 <- data.frame(a=c(NA,NA,NA,NA,NA), b=c(NA,NA,NA,NA,NA)) |> as_tibble()
  
```

\needspace{3\baselineskip}

`r if ((params$no_ecz == 1 & cztype == 'enroute') | (params$no_tcz == 1 & cztype == 'terminal')) "::: {.content-hidden}"`
## `r cztype_proper` charging zone - `r czname`
`r if ((params$no_ecz == 1 & cztype == 'enroute') | (params$no_tcz == 1 & cztype == 'terminal')) ":::"`


`r if ((params$no_ecz > 1 & cztype == 'enroute') | (params$no_tcz > 1 & cztype == 'terminal')) "::: {.content-hidden}"`
## `r cztype_proper` charging zone 
`r if ((params$no_ecz > 1 & cztype == 'enroute') | (params$no_tcz > 1 & cztype == 'terminal')) ":::"`

### Unit cost (KPI#1)

`r layout_2fig(paste0("chart_cef_duc_l2_", cztype, czindex), paste0("chart_cef_su_l2_", cztype, czindex))`


```{r chart_cef_cost_@@cz_type@@@@cz_index@@, options = (cz=c(czindex, cztype)), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level2_cef_cost.R
#| fig.align: "center"
#| fig-pos: "H"
```  


```{r table_level2_cef_cost_@@cz_type@@@@cz_index@@, options = (cz=c(czindex, cztype)), eval = (no_cz >= czindex)}
#| file: R/table_level2_cef_cost.R
#| include: false
```

``` {r, eval = (no_cz >= czindex), include = (no_cz >= czindex)}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table(
  title = paste0("Actual and determined data"),
  col_labels = c("Total costs - nominal (M€)", as.character(rp_years)),
  df = data_prep_pdf,
  col_align = "lrrrrr",
  col_widths = c(35, rep(65/5, 5))
))
```

\vspace{-20pt}

```{r table_level2_cef_cost_infl_@@cz_type@@@@cz_index@@, options = (cz=c(czindex, cztype)), eval = (no_cz >= czindex) }
#| file: R/table_level2_cef_cost_infl.R
#| include: false
```

``` {r, eval = (no_cz >= czindex), include = (no_cz >= czindex) }
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table(
  title = NA,
  df = data_prep,
  col_align = "lrrrrr",
  col_widths = c(35, rep(65/5, 5))
))
```

`r layout_2fig(paste0("chart_cef_cost_entity_", cztype, czindex), paste0("chart_cef_cost_main_", cztype, czindex))`


\needspace{3\baselineskip}

`\biggertext{Focus on unit cost}`{=latex}


**AUC vs. DUC**

\needspace{2\baselineskip}

**`r cztype_proper` service units**

\needspace{2\baselineskip}

**`r cztype_proper` costs by entity**

\needspace{2\baselineskip}

**`r cztype_proper` costs for the main ANSP at charging zone level**

```{r cef_txt_1_4_@@cz_type@@@@cz_index@@, results = "asis"}

```


### Actual unit cost incurred by the users (AUCU) (PI#1)

```{r chart_cef_aucu_@@cz_type@@@@cz_index@@, options = (cz=c(czindex, cztype)), include=(no_cz >= czindex), eval = (no_cz >= czindex)}
#| file: R/chart_level2_cef_aucu.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```  


```{r table_level2_cef_aucu_@@cz_type@@@@cz_index@@, options = (cz=c(czindex, cztype)), eval = (no_cz >= czindex)}
#| file: R/table_level2_cef_aucu.R
#| include: false
```

``` {r, eval = (no_cz >= czindex), include = (no_cz >= czindex)}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table(
  title = paste0("AUCU components (€/SU) – ", as.character(year_report)),
  df = data_prep_pdf,
  col_labels = c(paste0("Components of the AUCU in ", as.character(year_report)), 
             "€/SU"
             ),
  col_align = "lr",
  col_widths = c(80, 20),
  bold_data_rows = c(1,12,13)
))
```


```{r chart_cef_cex_@@cz_type@@@@cz_index@@, options = (cz=c(czindex, cztype)), include=(no_cz >= czindex), eval = no_cz >= czindex}
#| file: R/chart_level2_cef_cex.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```  


```{r table_level2_cef_cex_@@cz_type@@@@cz_index@@, options = (cz=c(czindex, cztype)), eval = (no_cz >= czindex)}
#| file: R/table_level2_cef_cex_tbv.R
#| include: false
```

``` {r, eval = (no_cz >= czindex), include = (no_cz >= czindex)}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table(
  title = paste0("Cost exempt from cost sharing – ", as.character(year_report)),
  df = data_prep_pdf,
  col_labels = c(paste0("Cost exempt from cost sharing by item - ", as.character(year_report)),
                         "€'000",
                        "€/SU"
  ),
  col_align = "lrr",
  col_widths = c(60, 20, 20),
  bold_data_rows = c(7)
))
```


### Regulatory result (RR)

`r layout_2fig(paste0("chart_cef_reg_res_", cztype, czindex), paste0("chart_cef_reg_res_aucu_", cztype, czindex))`

`r layout_2fig(paste0("chart_cef_reg_res_ansp_", cztype, czindex), paste0("chart_cef_net_res_main_ansp_", cztype, czindex))`

\needspace{3\baselineskip}

`\biggertext{Focus on regulatory result}`{=latex}


```{r cef_txt_1_13_@@cz_type@@@@cz_index@@, results = "asis"}
cat(quarto_paragraph_breaks(cef_level2_text$cef_txt_1_13[1,1]))
```

```{r cef_txt_1_10_txt_22_@@cz_type@@@@cz_index@@, results = "asis"}
cat(quarto_paragraph_breaks(cef_level2_text$cef_txt_1_10_txt))
```
