```{r cz_def_terminal3}
cz=c("3", "terminal")
  
# define cz
czindex <- as.numeric(cz[[1]])
cztype <- cz[[2]]

if (cztype == "enroute") {
  cztype_proper <- "En route"
  no_cz <- params$no_ecz
  czname <- ecz_list$ecz_name[[czindex]]
  cz_short <- 'er'
  
} else {
  cztype_proper <- "Terminal"
  no_cz <- params$no_tcz
  czname <- tcz_list$tcz_name[[czindex]]
  cz_short <- 'tz'
}

```

```{r chart_cef_duc_l2_terminal3, options = (cz=c(czindex, cztype,"level2")), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level1_cef.R
#| out.width: "100%"
```

```{r chart_cef_su_l2_terminal3, options = (cz=c(czindex, cztype)), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level2_cef_su.R
#| out.width: "100%"
```



```{r chart_cef_cost_entity_terminal3, options = (cz=c(czindex, cztype)), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level2_cef_cost_entity.R
#| out.width: "100%"
```

```{r chart_cef_cost_main_terminal3, options = (cz=c(czindex, cztype)), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level2_cef_cost_main.R
#| out.width: "100%"
```

<!-- #### Actual unit cost incurred by the users (AUCU) (PI#1) -->

<!-- #### Regulatory result (RR) -->

```{r chart_cef_reg_res_terminal3, options = (cz=c(czindex, cztype)), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level2_cef_reg_res.R
#| out.width: "100%"
```

```{r chart_cef_reg_res_aucu_terminal3, options = (cz=c(czindex, cztype)), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level2_cef_reg_res_aucu.R
#| out.width: "100%"
```

```{r chart_cef_reg_res_ansp_terminal3, options = (cz=c(czindex, cztype)), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level2_cef_reg_res_ansp.R
#| out.width: "100%"
```

```{r chart_cef_net_res_main_ansp_terminal3, options = (cz=c(czindex, cztype)), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level2_cef_net_res_main_ansp.R
#| out.width: "100%"
```


```{r cef-level2-headings-terminal3, eval = (params$country != "FABEC")}

source("R/get_level2_headings_cef.R")

```

\needspace{3\baselineskip}

`r if ((params$no_ecz == 1 & cztype == 'enroute') | (params$no_tcz == 1 & cztype == 'terminal')) "::: {.content-hidden}"`
## `r cztype_proper` charging zone - `r czname`
`r if ((params$no_ecz == 1 & cztype == 'enroute') | (params$no_tcz == 1 & cztype == 'terminal')) ":::"`


`r if ((params$no_ecz > 1 & cztype == 'enroute') | (params$no_tcz > 1 & cztype == 'terminal')) "::: {.content-hidden}"`
## `r cztype_proper` charging zone 
`r if ((params$no_ecz > 1 & cztype == 'enroute') | (params$no_tcz > 1 & cztype == 'terminal')) ":::"`

### Unit cost (KPI#1)

`r layout_2fig(paste0("chart_cef_duc_l2_", cztype, czindex), paste0("chart_cef_su_l2_", cztype, czindex))`


```{r chart_cef_cost_terminal3, options = (cz=c(czindex, cztype)), include=FALSE, eval = no_cz >= czindex}
#| file: R/chart_level2_cef_cost.R
#| fig.align: "center"
#| fig-pos: "H"
```  


```{r table_level2_cef_cost_terminal3, options = (cz=c(czindex, cztype)), eval = (no_cz >= czindex)}
#| file: R/table_level2_cef_cost.R
#| include: false
```

``` {r, eval = (no_cz >= czindex), include = (no_cz >= czindex)}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table(
  title = paste0("Actual and determined data"),
  col_labels = c("Total costs - nominal (M€)", as.character(rp_years)),
  df = data_prep_pdf,
  col_align = "lrrrrr",
  col_widths = c(35, rep(65/5, 5))
))
```

\vspace{-20pt}

```{r table_level2_cef_cost_infl_terminal3, options = (cz=c(czindex, cztype)), eval = (no_cz >= czindex) }
#| file: R/table_level2_cef_cost_infl.R
#| include: false
```

``` {r, eval = (no_cz >= czindex), include = (no_cz >= czindex) }
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table(
  title = NA,
  df = data_prep,
  col_align = "lrrrrr",
  col_widths = c(35, rep(65/5, 5))
))
```

`r layout_2fig(paste0("chart_cef_cost_entity_", cztype, czindex), paste0("chart_cef_cost_main_", cztype, czindex))`


\needspace{3\baselineskip}

`\biggertext{Focus on unit cost}`{=latex}

```{r}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cef_%s%d_1.qmd", as.character(year_report),country,country, as.character(year_report),cz_short, i)
replace_headings(path, cef_titles_s1)

# if (file.exists(path)) {cat(sprintf("{{< include %s >}}", path))}
``` 


### Actual unit cost incurred by the users (AUCU) (PI#1)

```{r chart_cef_aucu_terminal3, options = (cz=c(czindex, cztype)), include=(no_cz >= czindex), eval = (no_cz >= czindex)}
#| file: R/chart_level2_cef_aucu.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```  


```{r table_level2_cef_aucu_terminal3, options = (cz=c(czindex, cztype)), eval = (no_cz >= czindex)}
#| file: R/table_level2_cef_aucu.R
#| include: false
```

``` {r, eval = (no_cz >= czindex), include = (no_cz >= czindex)}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table(
  title = paste0("AUCU components (€/SU) – ", as.character(year_report)),
  df = data_prep_pdf,
  col_labels = c(paste0("Components of the AUCU in ", as.character(year_report)), 
             "€/SU"
             ),
  col_align = "lr",
  col_widths = c(80, 20),
  bold_data_rows = c(1,12,13)
))
```


```{r chart_cef_cex_terminal3, options = (cz=c(czindex, cztype)), include=(no_cz >= czindex), eval = no_cz >= czindex}
#| file: R/chart_level2_cef_cex.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```  


```{r table_level2_cef_cex_terminal3, options = (cz=c(czindex, cztype)), eval = (no_cz >= czindex)}
#| file: R/table_level2_cef_cex.R
```

``` {r, eval = (no_cz >= czindex), include = (no_cz >= czindex)}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table(
  title = paste0("Cost exempt from cost sharing – ", as.character(year_report)),
  df = data_prep_pdf,
  col_labels = c(paste0("Cost exempt from cost sharing by item - ", as.character(year_report)),
                         "€'000",
                        "€/SU"
  ),
  col_align = "lrr",
  col_widths = c(60, 20, 20),
  bold_data_rows = c(7)
))
```

\needspace{3\baselineskip}

`\biggertext{Focus on AUCU}`{=latex}

```{r}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cef_%s%d_2.qmd", as.character(year_report),country,country, as.character(year_report),cz_short, i)
replace_headings(path, cef_titles_s2)

``` 

### Regulatory result (RR)

`r layout_2fig(paste0("chart_cef_reg_res_", cztype, czindex), paste0("chart_cef_reg_res_aucu_", cztype, czindex))`

`r layout_2fig(paste0("chart_cef_reg_res_ansp_", cztype, czindex), paste0("chart_cef_net_res_main_ansp_", cztype, czindex))`

\needspace{3\baselineskip}

`\biggertext{Focus on regulatory result}`{=latex}

```{r}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cef_%s%d_3.qmd", as.character(year_report),country,country, as.character(year_report),cz_short, i)
replace_headings(path, cef_titles_s3)

``` 
