```{r env-level2-headings}
# placeholder for sourcing level 2 headings

```
::: {.grid .align-items-center}
:::: {.g-col-9}
[Environment - {{< var doc.country >}}]{.fakeh1}
::::

:::: {.g-col-3}
<span class="no-external-icon">[<i class="fa fa-download"></i> Download Report](`r params$home_address`/download/{{< var doc.year_report >}}/PRB-Annual-Monitoring-Report_{{< var doc.country >}}_{{< var doc.year_report >}}.pdf){.btn .btn-light .text-dark .border .bg-secondary-subtle .rounded}</span>
::::
:::


## PRB monitoring

```{r}
env_conc1 <- get_prb_conclusions(prb_findings_file, "environment", "Table_Findings_environment")
```

`r env_conc1`


`r if (params$country == "Luxembourg") "::: {.content-hidden}"`
::: {#container-er-performance}

## En route performance

### Horizontal flight efficiency of the actual trajectory ([**KEA**](`r params$home_address`/about.html#environment---horizontal-flight-efficiency-of-the-actual-trajectory-kea-kpi1-of-the-last-filed-flight-plan-kep-pi1-shortest-constrained-route-scr-pi2)) (KPI#1), of the last filed flight plan ([**KEP**](`r params$home_address`/about.html#environment---horizontal-flight-efficiency-of-the-actual-trajectory-kea-kpi1-of-the-last-filed-flight-plan-kep-pi1-shortest-constrained-route-scr-pi2)) (PI#1), shortest constrained route ([**SCR**](`r params$home_address`/about.html#environment---horizontal-flight-efficiency-of-the-actual-trajectory-kea-kpi1-of-the-last-filed-flight-plan-kep-pi1-shortest-constrained-route-scr-pi2)) (PI#2) and and vertical flight efficiency of the actual trajectory (PI#3)

:::: {layout="[ 50, 50 ]"}

::::: {.chart-container}  
```{r chart-env-kea, options = (doclevel=c("level2"))}
#| file: R/chart_level1_kea.R
#| out.width: "50%"
```
:::::

::::: {.chart-container}  
```{r chart-env-kea-month}
#| file: R/chart_level2_kea_month.R
#| out.width: "50%"
```
:::::

::::

:::: {layout="[ 50, 50 ]"}

::::: {.chart-container}  
```{r chart-env-kep-scr}
#| file: R/chart_level2_kep_scr.R
#| out.width: "100%"
```
:::::

::::: {.chart-container}  
```{r chart-env-kep-scr-month}
#| file: R/chart_level2_kep_scr_month.R
#| out.width: "100%"
```
:::::

::::

:::: {layout="[ 20, 60, 20 ]"}

::::: {#empty-div}
:::::

::::: {.chart-container}  
```{r chart-vfe, eval = (params$country != "Luxembourg")}
#| file: R/chart_level2_env_vfe_ert.R
#| out.width: "100%"
```
:::::
::::

:::
`r if (params$country == "Luxembourg") ":::"`




`r if (params$country == params$rp_full) "::: {.content-hidden}"`

`r if (params$no_tcz == 0) "::: {.content-hidden}"`

::: {#container-axot-asma}

## Terminal performance

### Additional taxi-out time ([**AXOT**](`r params$home_address`/about.html#environment---additional-taxi-out-time-axot-pi3-arrival-sequencing-and-metering-area-asma-time-pi4)) (PI#4), Additional taxi-in time ([**AXIT**](`r params$home_address`/about.html#environment---additional-taxi-out-time-axot-pi3-arrival-sequencing-and-metering-area-asma-time-pi4)) (PI#5) & Arrival Sequencing and Metering Area ([**ASMA**](`r params$home_address`/about.html#environment---additional-taxi-out-time-axot-pi3-arrival-sequencing-and-metering-area-asma-time-pi4)) time (PI#6)

:::: {layout="[ 20, 60, 20 ]"}

::::: {#empty-div}
:::::

::::: {.chart-container}  
```{r chart-axot-asma-country, eval = (params$country != params$rp_full)}
#| file: R/chart_level2_env_axot_asma_country.R
#| out.width: "100%"
```
:::::
::::


:::: {layout="[ 20, 60, 20 ]"}

::::: {#empty-div}
:::::

::::: {.chart-container}  
```{r chart-axot-apt}
#| file: R/chart_level2_env_axot_apt.R
#| out.width: "100%"
```
:::::

::::: {#empty-div}
:::::

::::
:::

::: {.callout-note collapse=true}

#### Focus on AXOT, AXIT & ASMA

**AXOT**

```{r env_trm_text_axot, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_trm_axot.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_trm_axot.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_trm_nsa_titles_axot)

``` 

**AXIT**

```{r env_trm_text_axit, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_trm_axit.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_trm_axit.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_trm_nsa_titles_axit)

``` 

**ASMA**

```{r env_trm_text_asma, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_trm_asma.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_trm_asma.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_trm_nsa_titles_asma)

``` 
:::

::: {#container-env-apt-pis}
:::: {#table-env-apt-pis}

```{r table-env-apt-pis, eval=!(params$no_tcz == 0 | params$country == params$rp_full)}
#| file: R/table_level2_env_apt_pis.R
#| out.width: "100%"
```

::::
:::


::: {#container-cdo}

### Average duration in climb ([**PI#7**](`r params$home_address`/about.html#environment---share-of-arrivals-applying-continuous-descent-operations-cdos-pi5)) and descent ([**PI#8**](`r params$home_address`/about.html#environment---share-of-arrivals-applying-continuous-descent-operations-cdos-pi5))

:::: {layout="[ 20, 60, 20 ]"}

::::: {#empty-div}
:::::

::::: {.chart-container}  
```{r chart-cdo-apt, eval = (params$no_tcz > 0)}
#| file: R/chart_level2_env_cdo_apt.R
#| out.width: "100%"
```
:::::
::::

:::

::: {.callout-note collapse=true}

#### Focus on average duration in descent and climb

**Average duration in descent**

```{r env_trm_text_vfed, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_trm_vfed.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_trm_vfed.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_trm_nsa_titles_vfed)

``` 

**Average duration in climb**


```{r env_trm_text_vfec, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_trm_vfec.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_trm_vfec.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_trm_nsa_titles_vfec)

``` 

:::

::: {#container-env-cdco-pis}
:::: {#table-env-cdco-pis}

```{r table-env-cdco-pis, eval=!(params$no_tcz == 0 | params$country == params$rp_full)}
#| file: R/table_level2_env_apt_pis_cdco.R
#| out.width: "100%"
```

::::
:::



`r if (params$no_tcz == 0) ":::"`


`r if (params$country == "Luxembourg") "::: {.content-hidden}"`
::: {#container-mil-pi}

## [**Civil-Military dimension**](`r params$home_address`/about.html#civil-military-dimension)  

:::: {layout="[ 20, 60, 20 ]"}

::::: {#empty-div}
:::::

::::: {.chart-container}  
```{r chart-ersa}
#| file: R/chart_level2_env_ersa.R
#| out.width: "100%"
```
:::::
::::

:::: {layout="[ 50, 50 ]"}

::::: {.chart-container}  
```{r chart-cdr}
#| file: R/chart_level2_env_cdr.R
#| out.width: "100%"
```
:::::

::::: {.chart-container}  
```{r chart-rsa}
#| file: R/chart_level2_env_rsa.R
#| out.width: "100%"
```
:::::

::::
:::

::: {.callout-note collapse=true}

#### Focus on Civil-Military dimension

**Effective use of reserved or segregated local airspace**

```{r env_mil_text_ersa}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_mil_ersa.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_mil_ersa.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_mil_nsa_titles_ersa)

``` 

**Rate of planning via available airspace structures**

```{r env_mil_text_rap}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_mil_rap.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_mil_rap.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_mil_nsa_titles_rap)

``` 

**Rate of using available airspace structures**

```{r env_mil_nsa_rau}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_mil_rau.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_mil_rau.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_mil_nsa_titles_rau)

``` 


:::
`r if (params$country == "Luxembourg") ":::"`
`r if (params$country == params$rp_full) ":::"`


`r if (params$country != params$rp_full) "::: {.content-hidden}"`
### Summary of performance at local level

:::: {layout="[ 20, 60, 20 ]"}

::::: {#empty-div}
:::::

::::: {.chart-container}  
```{r table-kea-summary}
#| file: R/table_env_kea_all_states.R
#| out.width: "100%"
```
:::::

::::: {#empty-div}
:::::

::::

`r if (params$country != params$rp_full) ":::"`
