---
pagetitle: "`r paste0('Safety - ', country)`"
title-block: false
---

::: {.grid .align-items-center}
:::: {.g-col-9}
[Safety - {{< var doc.country >}}]{.fakeh1}
::::

:::: {.g-col-3}
<span class="no-external-icon">[<i class="fa fa-download"></i> Download Report](`r params$home_address`/download/{{< var doc.year_report >}}/PRB-Annual-Monitoring-Report_{{< var doc.country >}}_{{< var doc.year_report >}}.pdf){.btn .btn-light .text-dark .border .bg-secondary-subtle .rounded}
</span>
::::
:::


## PRB monitoring
```{r concl-saf}
saf_conc1 <- get_prb_conclusions(prb_findings_file, "safety", "Table_Findings_safety")
```

`r saf_conc1`

::: {#container-saf-indicators}

## Effectiveness of Safety Management ([**EoSM**](`r params$home_address`/about.html#safety---effectiveness-of-safety-management-eosm-kpi1)) (KPI#1)

```{r, eval = params$country != params$rp_full}
#| label: chart_saf_eosm
#| out.width: "100%"
#| echo: false

source("R/chart_level1_saf.R")
```

`r if (params$no_saf_ansps >1) ":::: {.content-hidden}"`

::::: {layout="[ 20, 60, 20 ]"}

:::::: {#empty-div}
::::::

:::::: {.chart-container}  
```{r, eval = params$country != params$rp_full}
#| echo: false
mycharts[[1]]
```
::::::
:::::
`r if (params$no_saf_ansps >1) "::::"`


`r if (params$country == params$rp_full | params$no_saf_ansps == 1) ":::: {.content-hidden}"`
::::: {layout="[ 50, 50 ]"}

:::::: {.chart-container}  
```{r, eval = params$country != params$rp_full}
#| echo: false
mycharts[[1]]
```
:::::: 

:::::: {.chart-container}  
```{r, eval = (params$country != params$rp_full) & (params$no_saf_ansps > 1)}
#| echo: false
mycharts[[2]]
```
:::::: 
:::::
`r if (params$country == params$rp_full | params$no_saf_ansps == 1) "::::"`


`r if (params$country == params$rp_full | params$no_saf_ansps != 3) ":::: {.content-hidden}"`
::::: {layout="[ 25, 50, 25 ]"}

:::::: {#emptydiv}  
:::::: 

:::::: {.chart-container}  
```{r, eval = (params$country != params$rp_full) & (params$no_saf_ansps > 2)}
#| echo: false
mycharts[[3]]
```
:::::: 

:::::: {#emptydiv}  
:::::: 
:::::
`r if (params$country == params$rp_full | params$no_saf_ansps != 3) "::::"`


`r if (params$country == params$rp_full | params$no_saf_ansps != 4) ":::: {.content-hidden}"`
::::: {layout="[ 50, 50 ]"}

:::::: {.chart-container}  
```{r, eval = (params$country != params$rp_full) & (params$no_saf_ansps > 2)}
#| echo: false
mycharts[[3]]
```
:::::: 

:::::: {.chart-container}  
```{r, eval = (params$country != params$rp_full) & (params$no_saf_ansps > 3)}
#| echo: false
mycharts[[4]]
```
:::::: 
:::::
`r if (params$country == params$rp_full | params$no_saf_ansps != 4) "::::"`


`r if (params$country != params$rp_full) ":::: {.content-hidden}"`
::::: {layout="[ 50, 50 ]"}
:::::: {.chart-container}  
```{r chart_level2_saf_eosm_target_ses, eval = params$country == params$rp_full}
#| file: R/chart_level2_saf_eosm_target_ses.R
#| out.width: "100%"
```
::::::

:::::: {.chart-container}  
```{r chart_saf_ansp_ses, eval = params$country == params$rp_full}
#| file: R/chart_level1_saf_ses.R
#| out.width: "100%"
```
::::::
:::::

```{r chart_level2_saf_eosm_ses_allstates, eval= params$country == params$rp_full}
#| file: R/chart_level2_saf_eosm_ses_allstates.R
#| out.width: "100%"
```

::::: {layout="[ 55, 45 ]"}

:::::: {.chart-container}  
```{r chart_level2_saf_eosm_count_ses, eval= params$country == params$rp_full}
#| file: R/chart_level2_saf_eosm_count_ses.R
#| out.width: "100%"
```
:::::: 

:::::: {.chart-container}  
```{r chart_level2_saf_maturity_count_ses, eval= params$country == params$rp_full}
#| file: R/chart_level2_saf_maturity_count_ses.R
#| out.width: "100%"
```
:::::: 
:::::

`r if (params$country != params$rp_full) "::::"`


:::: {.callout-note collapse=true}

#### Focus on EoSM

```{r saf_text_eosm}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_saf_eosm.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::


## Safety occurrences

`r if (params$country == "MUAC") ":::: {.content-hidden}"`

### Rate of runway incursions ([**RIs**](`r params$home_address`/about.html#occurrences---rate-of-runway-incursions-ris-pi1-rate-of-separation-minima-infringements-smis-pi2)) (PI#1) and Rate of runway incursion with ANS contribution (PI#3)

:::: {layout="[ 45, 55 ]"}
::::: {.chart-container}  
```{r chart_saf_ri, eval= params$country != "MUAC"}
#| file: R/chart_level2_saf_ri.R
#| out.width: "100%"
```
:::::

::::: {.chart-container}  
```{r chart_level2_saf_ri_year_report, eval= (params$country != "MUAC"), options = (safindicator=c("ri"))}
#| file: R/chart_level2_saf_ri_smi_year_report.R
#| out.width: "100%"
```
:::::
::::

`r if (params$country != params$rp_full) ":::: {.content-hidden}"`
```{r chart_level2_saf_ri_per_state_ses, eval= (params$country == params$rp_full)}
#| file: R/chart_level2_saf_ri_per_state_ses.R
#| out.width: "100%"
```

```{r table_level2_saf_ri_apt_ses, eval= (params$country == params$rp_full)}
#| file: R/table_level2_saf_ri_apt_ses.R
#| out.width: "100%"
```
`r if (params$country != params$rp_full) "::::"`


:::: {layout="[ 5, 90, 5 ]"}
::::: {#emptydiv}  
:::::

::::: {.chart-container}  
```{r table_level2_saf_ri_apt, eval= (params$country != "MUAC") & (params$country != params$rp_full)}
#| file: R/table_level2_saf_ri_apt.R
#| out.width: "100%"
```
:::::

::::: {#emptydiv}  
:::::
::::

:::: {.callout-note collapse=true}

#### Focus on runway incursions

```{r saf_text_ri}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_saf_ri.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::

`r if (params$country == "MUAC") "::::"`

### Rate of separation minima infringements ([**SMIs**](`r params$home_address`/about.html#occurrences---rate-of-runway-incursions-ris-pi1-rate-of-separation-minima-infringements-smis-pi2)) (PI#2) and Rate of separation minima infringements with ANS contribution (PI#4)

:::: {layout="[ 45, 55 ]"}
::::: {.chart-container}  
```{r chart_saf_smi}
#| file: R/chart_level2_saf_smi.R
#| out.width: "100%"
```
:::::

::::: {.chart-container}  
```{r chart_level2_saf_smi_year_report, options = (safindicator=c("smi"))}
#| file: R/chart_level2_saf_ri_smi_year_report.R
#| out.width: "100%"
```
:::::
::::

`r if (params$country != params$rp_full) ":::: {.content-hidden}"`
```{r chart_level2_saf_smi_per_state_ses, eval= (params$country == params$rp_full)}
#| file: R/chart_level2_saf_smi_per_state_ses.R
#| out.width: "100%"
```

`r if (params$country != params$rp_full) "::::"`

```{r table_level2_saf_smi_ansp}
#| file: R/table_level2_saf_smi_ansp.R
#| out.width: "100%"
```


:::: {.callout-note collapse=true}

#### Focus on separation minima

```{r saf_text_smi}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_saf_smi.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::

### Quality of occurrences reporting 

```{r saf_text_occ}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_saf_occ.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

`r if (params$country == params$rp_full) ":::: {.content-hidden}"`


`r if (params$country == params$rp_full) "::::"`

:::





