::: {.grid .align-items-center}
:::: {.g-col-9}
[Annual Monitoring Report `r toupper(params$year_folder)` - {{< var doc.country >}}]{.fakeh1}
::::

:::: {.g-col-3}
<span class="no-external-icon">[<i class="fa fa-download"></i> Download Report](`r params$home_address`/download/{{< var doc.year_report >}}/PRB-Annual-Monitoring-Report_{{< var doc.country >}}_{{< var doc.year_report >}}.pdf){.btn .btn-light .text-dark .border .bg-secondary-subtle .rounded}</span>
::::
:::


```{r context-data, eval=TRUE}
cztype = "enroute"
cz = c("1", "enroute")

data_muac_raw  <-  read_xlsx(
  paste0(data_folder, "CEFF dataset master.xlsx"),
  sheet = "Enroute_T1",
  range = cell_limits(c(1, 1), c(NA, NA))) %>%
  as_tibble() %>% 
  clean_names()

if (year_folder == "rp3") {
  data_muac <- data_muac_raw |> 
  filter(grepl("MUAC", entity_code), status == "A") |> 
  mutate(
    entity_code = str_replace_all(entity_code, "_EB", ""),
    entity_code = str_replace_all(entity_code, "_EL", "")
    ) |> 
  group_by(entity_code) |> 
  summarise(x5_3_cost_nc2017 = sum(x5_3_cost_nc2017, na.rm = TRUE)) |> 
  ungroup()
  
} else {
data_muac <- data_muac_raw |> 
  filter(grepl("MUAC", entity_code), status == "A", year == year_report) |> 
  mutate(
    entity_code = str_replace_all(entity_code, "_EB", ""),
    entity_code = str_replace_all(entity_code, "_EL", "")
    ) |> 
  group_by(year, entity_code) |> 
  summarise(x5_3_cost_nc2017 = sum(x5_3_cost_nc2017, na.rm = TRUE)) |> 
  ungroup()
  
}

total_muac_costs <- sum(data_muac$x5_3_cost_nc2017, na.rm = TRUE)

share_EBEL <- paste0(round(pull(select(filter(data_muac, entity_code == "EBEL_MUAC"), x5_3_cost_nc2017)) / total_muac_costs *100,0), "%")
share_ED <- paste0(round(pull(select(filter(data_muac, entity_code == "ED_MUAC"), x5_3_cost_nc2017)) / total_muac_costs *100,0), "%")
share_EH <- paste0(round(pull(select(filter(data_muac, entity_code == "EH_MUAC"), x5_3_cost_nc2017)) / total_muac_costs *100,0), "%")

```

## Contextual information
::: columns
<!-- ******************* 1st column -->
:::: {.column width="50%"}

::::: columns
:::::: {.column width="60%"}
**Provision of ATC services in the upper**
**airspace across four States**
::::::

:::::: {.column width="40%"}
Belgium/Luxembourg<br>
Germany<br>
Netherlands
::::::
:::::

::::: columns
:::::: {.column width="20%"}
**ACC**
::::::

:::::: {.column width="80%"}
Maastricht UAC
::::::
:::::
::::

<!-- ******************* 2nd column -->
:::: {.column width="50%"}

**Allocation of actual en route costs **

::::: columns
:::::: {.column width="20%"}
::::::

:::::: {.column width="50%"}
Belgium/Luxembourg<br>
Germany<br>
Netherlands
::::::

:::::: {.column width="30%"}
`r share_EBEL`<br>
`r share_ED`<br>
`r share_EH`
::::::
:::::

::::

:::



## Safety

```{r chart-saf-code}
#| label: chart_saf_eosm
#| out.width: "100%"
#| echo: false

source("R/chart_level1_saf.R")
```

::: {#container-saf1}
:::: {#chart-saf class="mychart"}
```{r chart-saf}
#| echo: false
mycharts[[1]]
```
::::

:::: {#concl-eosm}
```{r concl-eosm}
saf_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "safety", "Table_Findings_safety")
```

`r saf_conc1`
::::
:::

::: {#container-cap style="clear: both"}

## Capacity
<!-- empty line to ensure next heading leaves enough space -->
<div style="height: 1px"></div>

:::: {#chart-cap class="mychart"}
```{r chart-cap-er}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```
::::

:::: {#concl-cap}
```{r concl-cap}
cap_er_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "ER_capacity", "Table_Findings_ER_capacity")
```

`r cap_er_conc1`
::::
:::

::: {#container-cef style="clear: both"}
<!-- empty line to ensure next heading leaves enough space -->
<div style="height: 1px"></div>

## Cost-efficiency

:::: {#chart-cef class="mychart"}
```{r chart-cef}
#| file: R/chart_level2_cef_cost.R
#| out.width: "100%"
```
::::

:::: {#concl-cef}
```{r concl-cef}
cef_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "cost-efficiency", "Table_Findings_CEFF")
```

`r cef_conc1`
::::
:::