<!-- Level1 -->
```{r chart_cap_er, options = (cztype=c("enroute")), include = FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

```{r chart_cap_trm, options = (cztype=c("terminal")), include = FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```


```{r chart_level1_cef_er_ses, include = FALSE}
#| file: R/chart_level1_cef_er_ses.R
#| out.width: "100%"
```

```{r chart_cef_trm_1, options = (cz=c("1", "terminal", "level1")), include = FALSE}
#| file: R/chart_level1_cef.R
#| out.width: "100%"
```


<!-- Level2 -->
<!-- ## Safety -->
<!-- ## Actual versus planned number of ANSPs achieving the level of the EoSM targets for RP3 -->
```{r chart_level2_saf_eosm_target_ses, include=FALSE}
#| file: R/chart_level2_saf_eosm_target_ses.R
#| out.width: "100%"
```


```{r chart_level2_saf_eosm_count_ses, include=FALSE}
#| file: R/chart_level2_saf_eosm_count_ses.R
#| out.width: "100%"
```

```{r chart_level2_saf_maturity_count_ses, include=FALSE}
#| file: R/chart_level2_saf_maturity_count_ses.R
#| out.width: "100%"
```

<!-- ### Occurrences - Rate of runway incursions (RIs) (PI#1)  -->

```{r chart_saf_ri, include=FALSE}
#| file: R/chart_level2_saf_ri.R
#| out.width: "100%"
```

```{r chart_level2_saf_ri_year_report, options = (safindicator=c("ri")), include=FALSE}
#| file: R/chart_level2_saf_ri_smi_year_report.R
#| out.width: "100%"
```

<!-- ### Rate of separation minima infringements (SMIs) (PI#2) -->
```{r chart_saf_smi, include=FALSE}
#| file: R/chart_level2_saf_smi.R
#| out.width: "100%"
```

```{r chart_level2_saf_smi_year_report, options = (safindicator=c("smi")), include=FALSE}
#| file: R/chart_level2_saf_ri_smi_year_report.R
#| out.width: "100%"
```

<!-- ## ENVIRONMENT -->
<!-- ### En route performance -->
<!-- #### Horizontal flight efficiency of the actual trajectory (KEA) (KPI#1), of the last filed flight plan (KEP) (PI#1) & shortest constrained route (SCR) (PI#2) -->

```{r chart_env_kea_l2, options = (doclevel=c("level2")), include=FALSE}
#| file: R/chart_level1_kea.R
#| out.width: "100%"
```

```{r chart_env_kea_month, include=FALSE}
#| file: R/chart_level2_kea_month.R
#| out.width: "100%"
```

```{r chart_env_kep_scr, include=FALSE}
#| file: R/chart_level2_kep_scr.R
#| out.width: "100%"
```

```{r chart_env_kep_scr_month, include=FALSE}
#| file: R/chart_level2_kep_scr_month.R
#| out.width: "100%"
```


<!-- ## CAPACITY -->
<!-- ### En route performance -->
<!-- #### En route ATFM delay (KPI#1) -->
```{r chart_cap_er_l2, options = (cztype=c("enroute")), include=FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

```{r chart_cap_er_month, options = (cztype=c("enroute")), include=FALSE}
#| file: R/chart_level2_cap_month.R
#| out.width: "100%"
```

<!-- En route perfromance indicators at ACC level (PI#3-4) -->

```{r chart_level2_cap_perc_delay_above, eval=(params$country != "Luxembourg"), include=FALSE}
#| file: R/chart_level2_cap_perc_delay_above.R
#| out.width: "100%"
```


```{r chart_level2_cap_peak_tp, eval=(params$country != "Luxembourg"), include=FALSE}
#| file: R/chart_level2_cap_peak_tp.R
#| out.width: "100%"
```

<!-- #### Other indicators -->

```{r chart_cap_atco, include=FALSE}
#| file: R/chart_level2_cap_atco.R
#| out.width: "100%"
```

```{r chart_cap_sector_opening_ses, include=FALSE}
#| file: R/chart_level2_cap_sector_opening.R
#| out.width: "100%"
```

<!-- #### Arrival ATFM delay (KPI#2) -->
```{r chart_cap_trm_l2, options = (cztype=c("terminal")), include=FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

```{r chart_cap_trm_month, options = (cztype=c("terminal")), include=FALSE}
#| file: R/chart_level2_cap_month.R
#| out.width: "100%"
```

<!-- En route charging zone -->
```{r chart_cef_duc_er_ses, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level1_cef_er_ses.R
#| out.width: "100%"
```

```{r chart_cef_su, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_su.R
#| out.width: "100%"
```

<!-- AUCU -->

<!-- regulatory result -->
```{r chart_cef_reg_res, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_reg_res.R
#| out.width: "100%"
```

```{r chart_cef_reg_res_aucu,  options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_reg_res_aucu.R
#| out.width: "100%"
```

```{r chart_cef_reg_res_ansp, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_reg_res_ansp.R
#| out.width: "100%"
```

```{r chart_cef_net_res_main_ansp, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_net_res_main_ansp.R
#| out.width: "100%"
```

<!-- Terminal charging zone -->
```{r chart_cef_duc_tz_ses, options = (cz=c("1", "terminal")), include=FALSE}
#| file: R/chart_level1_cef_er_ses.R
#| out.width: "100%"
```

```{r chart_cef_su_tz, options = (cz=c("1", "terminal")), include=FALSE}
#| file: R/chart_level2_cef_su.R
#| out.width: "100%"
```

<!-- AUCU -->

<!-- regulatory result -->
```{r chart_cef_reg_res_tz, options = (cz=c("1", "terminal")), include=FALSE}
#| file: R/chart_level2_cef_reg_res.R
#| out.width: "100%"
```

```{r chart_cef_reg_res_aucu_tz,  options = (cz=c("1", "terminal")), include=FALSE}
#| file: R/chart_level2_cef_reg_res_aucu.R
#| out.width: "100%"
```

```{r chart_cef_reg_res_ansp_tz, options = (cz=c("1", "terminal")), include=FALSE}
#| file: R/chart_level2_cef_reg_res_ansp.R
#| out.width: "100%"
```

```{r chart_cef_net_res_main_ansp_tz, options = (cz=c("1", "terminal")), include=FALSE}
#| file: R/chart_level2_cef_net_res_main_ansp.R
#| out.width: "100%"
```


# OVERVIEW

## Contextual information
```{r fetch-data-ses, eval=TRUE}
data_context <-readxl::read_xlsx(
  paste0(data_folder, ses_data_file),
  sheet = "Context",
  range = cell_limits(c(1, 1), c(NA, NA))) %>%
  as_tibble() %>% 
  clean_names() %>% 
  filter(year_report == .env$year_report & year == .env$year_report)

acc_no_context <- data_context %>% select(number_of_acc) %>% pull()
no_apt_big_context <- data_context %>% select(no_apts_big) %>% pull()
no_apt_small_context <- data_context %>% select(no_apts_small) %>% pull()

ert_trm_share_context <- data_context %>% select(ert_trm_share) %>% pull()
ert_cz_context <- data_context %>% select(ert_cz) %>% pull()
trm_cz_context <- data_context %>% select(trm_cz) %>% pull()

main_ansp_context <- data_context %>% select(main_ans_ps_ert) %>% pull()
other_ansp_context <- data_context %>% select(other_ans_ps_ert) %>% pull()
met_ansp_context <- data_context %>% select(met_providers) %>% pull()
```

::: {layout="[ 34, 38, 28 ]"}

::::{#1st-column}
**No of ACCs   ** `r acc_no_context`  
```{=tex}
\par\vspace{1em}
```

**No of airports in the scope**
```{=tex}
```
**of the performance plan:**

- **≥80'K     ** `r no_apt_big_context`
- **<80'K     ** `r no_apt_small_context`

::::

::::{#2nd-column}
```{=tex}
\vspace*{-\baselineskip} % Adjust vertical alignment to the top
```
**Share en route / terminal**
```{=tex}
```
**costs `r year_report`                 ** `r ert_trm_share_context`
```{=tex}
\par\vspace{1em}
```
**En route charging zone(s)     ** `r ert_cz_context`
```{=tex}
\par\vspace{1em}
```
**Terminal charging zone(s)    ** `r trm_cz_context`
::::

::::{#3rd-column}
```{=tex}
\vspace*{-\baselineskip} % Adjust vertical alignment to the top
\vspace{-1.5em}
```
**No of main ANSPs     ** `r main_ansp_context`
```{=tex}
\par\vspace{1em}
```
**No of other ANSPs    ** `r other_ansp_context`
```{=tex}
\par\vspace{1em}
```
**No of MET Providers ** `r met_ansp_context`
::::

:::


## Main PRB findings - `r year_folder`

[Placeholder for text]

## Traffic (`r rp_full` area)

```{r chart_level1_traffic_mvt}
#| file: R/chart_level1_traffic_mvt.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

```{r mvt_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_ifr_movements.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

```{r chart_level1_traffic_su}
#| file: R/chart_level1_traffic_su.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

```{r tsu_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_service_units.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

## Safety (`r rp_full` area)

```{r chart_level1_saf_ses}
#| file: R/chart_level1_saf_ses.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

```{r saf_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_saf.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

## Environment (`r rp_full` area)

```{r chart_env_kea, options = (doclevel=c("level1"))}
#| file: R/chart_level1_kea.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

```{r env_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_env.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

## Capacity (`r rp_full` area)

`r layout_2fig("chart_cap_er", "chart_cap_trm")`

```{r cap_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_cap.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

## Cost-efficiency (`r rp_full` area)

`r layout_2fig("chart_level1_cef_er_ses", "chart_cef_trm_1")`

```{r cef_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_cef.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

\needspace{3\baselineskip}

`r if (year_folder == rp_summary_year) "::: {.content-hidden}"`

# SAFETY - `r rp_full`

## PRB monitoring

```{r saf_prb2}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_saf.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

## Actual versus planned number of ANSPs achieving the level of the EoSM targets for RP3 ahead of 2024

`r layout_2fig("chart_level1_saf_ses", "chart_level2_saf_eosm_target_ses")`

```{r chart_level2_saf_eosm_ses_allstates, eval=(year_folder != params$rp_summary_year)}
#| file: R/chart_level2_saf_eosm_ses_allstates.R
#| out.width: "100%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r layout_2fig("chart_level2_saf_eosm_count_ses", "chart_level2_saf_maturity_count_ses", width1 = 0.65, width2 = 0.30)`

\needspace{3\baselineskip}

\biggertext{Focus on EoSM}

```{r saf_text_eosm}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_saf_eosm.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

\needspace{2\baselineskip}


## Rate of runway incursions (RIs) (PI#1) and Rate of runway incursion with ANS contribution (PI#3)

`r layout_2fig("chart_saf_ri", "chart_level2_saf_ri_year_report")`

```{r chart_level2_saf_ri_per_state_ses, eval=(year_folder != params$rp_summary_year)}
#| file: R/chart_level2_saf_ri_per_state_ses.R
#| out.width: "100%"
#| fig.align: "center"
#| fig-pos: "H"
```

```{r table_level2_saf_ri_apt_ses, eval=(year_folder != params$rp_summary_year)}
#| file: R/table_level2_saf_ri_apt_ses.R
#| include: false
```


``` {r table_level2_saf_ri_apt_ses_p, eval=(year_folder != params$rp_summary_year)}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table_2level(
  title = paste0("Rate of RI per 100,000 airport movements"),
  df = data_prep_pdf,
  # col_labels = rep(c("#", "Mvts.", "Airport", "Total RI", "RI per 1000 mvts."),3),
  body_fontsize = c(8, 9.6),
  col_align = "llrrrllrrrllrrr",
  col_widths_pct = c(3,10,8,5,8, 3,10,8,5,8, 3,10,6,5,8),
  cell_pad_em = 0.4,       
  wrap_raw_block = FALSE,
  header_row_height_ex = 2.4,
  row_extrarowheight_pt = 2 
))
```

\needspace{3\baselineskip}


\biggertext{Focus on runway incursions}

```{r saf_text_ri}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_saf_ri.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

```


\needspace{2\baselineskip}


## Rate of separation minima infringements (SMIs) (PI#2) and Rate of separation minima infringements with ANS contribution (PI#4)

`r layout_2fig("chart_saf_ri", "chart_level2_saf_smi_year_report")`

```{r chart_level2_saf_smi_per_state_ses, eval=(year_folder != params$rp_summary_year)}
#| file: R/chart_level2_saf_smi_per_state_ses.R
#| out.width: "100%"
#| fig.align: "center"
#| fig-pos: "H"
```

```{r table_level2_saf_smi_ansp_pdf1, eval=(year_folder != params$rp_summary_year)}
#| file: R/table_level2_saf_smi_ansp_pdf1.R
#| include: false
```


``` {r table_level2_saf_smi_ansp_pdf1_p, eval=(year_folder != params$rp_summary_year)}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table_2level(
  title = paste0("Rate of SMI with ANS contribution per 100,000 flight hours"),
  df = data_prep,
  col_align = "llrrrrrrrrrr",
  col_widths = c(4,11,rep(8.5,10)),
  body_fontsize = c(8, 10),
  cell_pad_em = 0.3,
  wrap_raw_block = FALSE,
  header_row_height_ex = 2.4,
  row_extrarowheight_pt = 2 
))
```

\vspace{-20pt}

```{r table_level2_saf_smi_ansp_pdf2, eval=(year_folder != params$rp_summary_year)}
#| file: R/table_level2_saf_smi_ansp_pdf2.R
#| include: false
```

``` {r table_level2_saf_smi_ansp_pdf2_p, eval=(year_folder != params$rp_summary_year)}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table_2level(
  title = NA,
  df = data_prep,
  col_align = "llrrrrrrrrrr",
  col_widths = c(4,11,rep(8.5,10)),
  body_fontsize = c(8, 10),
  cell_pad_em = 0.3,
  wrap_raw_block = FALSE,
  header_row_height_ex = 2.4,
  row_extrarowheight_pt = 2 
))
```



\needspace{3\baselineskip}


\biggertext{Focus on separation minima}

```{r saf_text_smi}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_saf_smi.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 


\needspace{2\baselineskip}

# ENVIRONMENT - `r rp_full`

## PRB monitoring

```{r env_prb2}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_env.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

\needspace{3\baselineskip}

## En route performance

### Horizontal flight efficiency of the actual trajectory (KEA) (KPI#1), of the last filed flight plan (KEP) (PI#1) , shortest constrained route (KES) (PI#2) and vertical flight efficiency of the actual trajectory (VFE) (PI#3)

`r layout_2fig("chart_env_kea_l2", "chart_env_kea_month")`

`r layout_2fig("chart_env_kep_scr", "chart_env_kep_scr_month")`

```{r chart_vfe, eval=(params$country != "Luxembourg")}
#| file: R/chart_level2_env_vfe_ert.R
#| out.width: "50%"
#| fig.align: "center"
#| fig-pos: "H"
```

\needspace{3\baselineskip}

### Summary of performance at local level

```{r table_kea_summary, eval=(year_folder != params$rp_summary_year)}
#| file: R/table_env_kea_all_states.R
#| include: false
```

``` {r table_kea_summary_p, eval=(year_folder != params$rp_summary_year)}
#| echo: false
#| results: asis
cat(make_quarto_latex_table(
  title = "KEA (%)",
  df = data_prep_pdf,
  col_labels = c("State", "Target", "Actual", " "),
  col_align = "lrrc",
  col_widths = c(35, 30, 30,5),
  checkmarks = c(4)

))
```

\biggertext{Focus on en route performance}

```{r env_er_text_kea}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_er_kea.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

\needspace{3\baselineskip}

## Civil-Military dimension

```{r chart_ersa}
#| file: R/chart_level2_env_ersa.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r layout_2fig("chart_cdr", "chart_rsa")`


\needspace{3\baselineskip}

# CAPACITY - `r rp_full`

## PRB monitoring

```{r cap_prb2}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_cap.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

\needspace{3\baselineskip}

## En route performance

### En route ATFM delay (KPI#1)

`r layout_2fig("chart_cap_er_l2", "chart_cap_er_month")`

```{r chart_cap_delay_bin, eval=(year_folder != params$rp_summary_year)}
#| file: R/chart_level2_cap_delay_bin.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

\needspace{3\baselineskip}

\biggertext{Focus on en route ATFM delay}

```{r cap_er_text_atfm }
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_er_atfm.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))
``` 

\needspace{3\baselineskip}

### Summary of performance at local level

```{r table_cap_erdelay_summary, eval=(year_folder != params$rp_summary_year)}
#| file: R/table_cap_erdelay_all_states.R
#| include: false
```


``` {r table_cap_erdelay_summary_p, eval=(year_folder != params$rp_summary_year)}
#| echo: false
#| results: asis
cat(make_quarto_latex_table(
  title = "En route delay (min/flight)",
  df = data_prep_pdf,
  col_labels = c("State", "Target", "Actual", ""),
  col_align = "lrrc",
  col_widths = c(35, 30, 30,5),
  checkmarks = c(4)

))
```

\needspace{3\baselineskip}

\biggertext{Focus on performance at local level}

```{r cap_er_text_summary}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_er_summary.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

\needspace{3\baselineskip}

### Other en route information

`r layout_2fig("chart_cap_atco", "chart_cap_sector_opening_ses")`

\needspace{3\baselineskip}

\biggertext{Focus on other en route information}

```{r cap_er_text_other}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_er_other.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 


\needspace{3\baselineskip}

## Terminal performance

### Arrival ATFM delay (PI#1)

`r layout_2fig("chart_cap_trm_l2", "chart_cap_trm_month")`

### Summary of performance at local level

```{r table_cap_arrdelay_summary, eval=(year_folder != params$rp_summary_year)}
#| file: R/table_cap_arrdelay_all_states.R
#| include: false
```


``` {r table_cap_arrdelay_summary_p, eval=(year_folder != params$rp_summary_year)}
#| echo: false
#| results: asis
cat(make_quarto_latex_table(
  title = "Arrival delay (min/flight)",
  df = data_prep_pdf,
  col_labels = c("State", "Target", "Actual", ""),
  col_align = "lrrc",
  col_widths = c(35, 30, 30,5),
  checkmarks = c(4)

))
```

\needspace{3\baselineskip}

\biggertext{Focus on arrival ATFM delay}

```{r cap_trm_text_atfm}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_trm_atfm.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))
``` 

\needspace{3\baselineskip}


### Other terminal performance indicators

```{r chart_cap_all_causes_delay_ses, eval=(year_folder != params$rp_summary_year)}
#| file: R/chart_level2_cap_all_causes_delay.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

\needspace{3\baselineskip}

\biggertext{Focus on other terminal performance indicators}

```{r cap_er_text_trm_other}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_trm_other.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

```

\needspace{3\baselineskip}

# COST-EFFICIENCY - `r rp_full`

## PRB monitoring

```{r cef_prb2}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_cef.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

## En route charging zone

`r layout_2fig("chart_cef_duc_er_ses", "chart_cef_su")`

```{r chart_cef_cost, options = (cz=c("1", "enroute")), eval=(year_folder != params$rp_summary_year)}
#| file: R/chart_level2_cef_cost.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```


```{r table_cef_cost, options = (cz=c("1", "enroute")), eval=(year_folder != params$rp_summary_year)}
#| file: R/table_level2_cef_cost.R
#| include: false
```

``` {r table_cef_cost_p, eval=(year_folder != params$rp_summary_year)}
#| echo: false
#| results: asis
cat(make_quarto_latex_table(
  title = paste0("Actual and determined data"),
  col_labels = c("Total costs - nominal (M€)", as.character(rp_years)),
  df = data_prep_pdf,
  col_align = "lrrrrr",
  col_widths = c(35, rep(65/5, 5))
))
```


### Summary of performance at local level

:::: {#table-cef-summary}
```{r table_cef_summary, options = (cztype="enroute"), eval=(year_folder != params$rp_summary_year)}
#| file: R/table_cef_summary.R
#| out.width: "100%"
#| fig-asp: 1
```
::::

\needspace{3\baselineskip}

\biggertext{Focus on unit cost}

```{r}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cef_%s%d_1.qmd", as.character(year_report),
                country,
                country,
                as.character(year_report),
                'er',
                7
)

replace_headings(path, character(0))
  
``` 

\needspace{3\baselineskip}

### Actual unit cost incurred by the users (AUCU) (PI#1)

```{r chart_cef_aucu_enroute, options = (cz=c("1", "enroute")), eval=(year_folder != params$rp_summary_year)}
#| file: R/chart_level2_cef_aucu.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```  

```{r table_level2_cef_aucu_enroute, options = (cz=c("1", "enroute")), eval=(year_folder != params$rp_summary_year)}
#| file: R/table_level2_cef_aucu.R
#| include: false
```

``` {r table_level2_cef_aucu_enroute_p, eval=(year_folder != params$rp_summary_year)}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table(
  title = paste0("AUCU components (€/SU) – ", as.character(year_report)),
  df = data_prep_pdf,
  col_labels = c(paste0("Components of the AUCU in ",
                        as.character(year_report)), 
             "€/SU"
             ),
  col_align = "lr",
  col_widths = c(80, 20),
  bold_data_rows = c(1,12,13)
))
```


```{r chart_cef_cex_enroute, R.options = (cz=c("1", "enroute")), eval=(year_folder != params$rp_summary_year)}
#| file: R/chart_level2_cef_cex.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```  


```{r table_level2_cef_cex_enroute, R.options = (cz=c("1", "enroute")), eval=(year_folder != params$rp_summary_year)}
#| file: R/table_level2_cef_cex.R
#| include: false
```

``` {r table_level2_cef_cex_enroute_p, eval=(year_folder != params$rp_summary_year)}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table(
  title = NA,
  df = data_prep_pdf,
  col_labels = c(paste0("Cost exempt from cost sharing by item - ",
                        as.character(year_report)),
                         "€'000",
                        "€/SU"
  ),
  col_align = "lrr",
  col_widths = c(60, 20, 20),
  bold_data_rows = c(7)
))
```


\needspace{3\baselineskip}

\biggertext{Focus on AUCU}

```{r}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cef_%s%d_2.qmd", as.character(year_report),
                country,
                country,
                as.character(year_report),
                'er',
                7
)

replace_headings(path, character(0))
  
``` 

\needspace{3\baselineskip}

### Regulatory result (RR)

`r layout_2fig("chart_cef_reg_res", "chart_cef_reg_res_aucu")`

`r layout_2fig("chart_cef_reg_res_ansp", "chart_cef_net_res_main_ansp")`

\needspace{3\baselineskip}

\biggertext{Focus on regulatory result}

```{r}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cef_%s%d_3.qmd", as.character(year_report),
                country,
                country,
                as.character(year_report),
                'er',
                7
)

replace_headings(path, character(0))
  
``` 

## Terminal charging zone

`r layout_2fig("chart_cef_duc_tz_ses", "chart_cef_su_tz")`

```{r chart_cef_cost_tz, options = (cz=c("1", "terminal")), eval=(year_folder != params$rp_summary_year)}
#| file: R/chart_level2_cef_cost.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```


```{r table_cef_cost_tz, options = (cz=c("1", "terminal")), eval=(year_folder != params$rp_summary_year)}
#| file: R/table_level2_cef_cost.R
#| include: false
```

``` {r table_cef_cost_p_tz, eval=(year_folder != params$rp_summary_year)}
#| echo: false
#| results: asis
cat(make_quarto_latex_table(
  title = paste0("Actual and determined data"),
  col_labels = c("Total costs - nominal (M€)", as.character(rp_years)),
  df = data_prep_pdf,
  col_align = "lrrrrr",
  col_widths = c(35, rep(65/5, 5))
))
```


### Summary of performance at local level

:::: {#table-cef-summary}
```{r table_cef_summary_tz, options = (cztype="terminal"), eval=(year_folder != params$rp_summary_year)}
#| file: R/table_cef_summary.R
#| out.width: "100%"
#| fig-asp: 1
```
::::

\needspace{3\baselineskip}


### Actual unit cost incurred by the users (AUCU) (PI#1)

```{r chart_cef_aucu_tz, options = (cz=c("1", "terminal")), eval=(year_folder != params$rp_summary_year)}
#| file: R/chart_level2_cef_aucu.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```  

```{r table_level2_cef_aucu_tz, options = (cz=c("1", "terminal")), eval=(year_folder != params$rp_summary_year)}
#| file: R/table_level2_cef_aucu.R
#| include: false
```

``` {r table_level2_cef_aucu_enroute_p_tz, eval=(year_folder != params$rp_summary_year)}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table(
  title = paste0("AUCU components (€/SU) – ", as.character(year_report)),
  df = data_prep_pdf,
  col_labels = c(paste0("Components of the AUCU in ",
                        as.character(year_report)), 
             "€/SU"
             ),
  col_align = "lr",
  col_widths = c(80, 20),
  bold_data_rows = c(1,12,13)
))
```


```{r chart_cef_cex_tz, R.options = (cz=c("1", "terminal")), eval=(year_folder != params$rp_summary_year)}
#| file: R/chart_level2_cef_cex.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```  


```{r table_level2_cef_cex_tz, R.options = (cz=c("1", "terminal")), eval=(year_folder != params$rp_summary_year)}
#| file: R/table_level2_cef_cex.R
#| include: false
```

``` {r table_level2_cef_cex_enroute_p_tz, eval=(year_folder != params$rp_summary_year)}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table(
  title = NA,
  df = data_prep_pdf,
  col_labels = c(paste0("Cost exempt from cost sharing by item - ",
                        as.character(year_report)),
                         "€'000",
                        "€/SU"
  ),
  col_align = "lrr",
  col_widths = c(60, 20, 20),
  bold_data_rows = c(7)
))
```


\needspace{3\baselineskip}

### Regulatory result (RR)

`r layout_2fig("chart_cef_reg_res_tz", "chart_cef_reg_res_aucu_tz")`

`r layout_2fig("chart_cef_reg_res_ansp_tz", "chart_cef_net_res_main_ansp_tz")`

`r if (year_folder == params$rp_summary_year) ":::"`
