::: {.grid .align-items-center}
:::: {.g-col-9}
[Annual Monitoring Report `r toupper(params$year_folder)` - {{< var doc.country >}}]{.fakeh1}
::::

:::: {.g-col-3}
<span class="no-external-icon">[<i class="fa fa-download"></i> Download Report](`r params$home_address`/download/{{< var doc.year_report >}}/PRB-Annual-Monitoring-Report_{{< var doc.country >}}_{{< var doc.year_report >}}.pdf){.btn .btn-light .text-dark .border .bg-secondary-subtle .rounded}</span>
::::
:::

## Contextual information
```{r fetch-data-ses, eval=TRUE}
data_context_raw <- readxl::read_xlsx(
  paste0(data_folder, ses_data_file),
  sheet = "Context",
  range = cell_limits(c(1, 1), c(NA, NA))) %>%
  as_tibble() %>% 
  clean_names() 

if (year_folder == rp_summary_year) {
  data_context <- data_context_raw %>% 
    filter(year_report == .env$year_report) %>% 
    summarise(
      number_of_acc = max(number_of_acc, na.rm = TRUE),
      no_apts_big = min(no_apt_big, na.rm = TRUE),
      no_apts_small = max(no_apt_small, na.rm = TRUE),
      
      ert_cz = max(ert_cz, na.rm = TRUE),
      trm_cz = max(trm_cz, na.rm = TRUE),
      
      main_ans_ps_ert = max(main_ans_ps_ert, na.rm = TRUE),
      other_ans_ps_ert = max(other_ans_ps_ert, na.rm = TRUE),
      met_providers = max(met_providers, na.rm = TRUE),
      
      en_route_costs = sum(en_route_costs, na.rm = TRUE),
      terminal_costs = sum(terminal_costs, na.rm = TRUE)
      
    ) %>% 
      mutate(
        ert_trm_share = paste0(
          format(janitor::round_half_up(en_route_costs/(en_route_costs + terminal_costs)*100, 0), nsmall = 0),
          "% / ",
                   format(janitor::round_half_up(terminal_costs/(en_route_costs + terminal_costs)*100, 0), nsmall = 0),
          "%"
        )
      )

} else {
  data_context <- data_context_raw %>% 
    filter(year_report == .env$year_report & year == .env$year_report)
}

acc_no <- data_context %>% select(number_of_acc) %>% pull()
no_apt_big <- data_context %>% select(no_apts_big) %>% pull()
no_apt_small <- data_context %>% select(no_apts_small) %>% pull()

ert_trm_share <- data_context %>% select(ert_trm_share) %>% pull()
ert_cz <- data_context %>% select(ert_cz) %>% pull()
trm_cz <- data_context %>% select(trm_cz) %>% pull()

main_ansp <- data_context %>% select(main_ans_ps_ert) %>% pull()
other_ansp <- data_context %>% select(other_ans_ps_ert) %>% pull()
met_ansp <- data_context %>% select(met_providers) %>% pull()
```


::: columns
<!-- ******************* 1st column -->
:::: {.column width="34%"}
**No of ACCs  ** `r acc_no`

::::: columns
:::::: {.column width="60%"}
**No of airports in the scope of the performance plan**
::::::

:::::: {.column width="40%"}
**≥80'K    ** `r no_apt_big`<br/> **<80'K     ** `r no_apt_small`
::::::
:::::
::::

<!-- ******************* 2nd column -->
:::: {.column width="38%"}

**Share en route / terminal costs `r toupper(params$year_folder)`  ** `r ert_trm_share`

::::: columns
:::::: {.column width="55%"}
**En route charging zone(s)**
::::::

:::::: {.column width="45%"}
`r ert_cz`
::::::
:::::

::::: columns
:::::: {.column width="55%"}
[**Terminal charging zone(s)**]{.context-text}
::::::

:::::: {.column width="45%"}
`r trm_cz`
::::::
:::::
::::

<!-- ******************* 3rd column -->
:::: {.column width="28%"}
::::: columns
:::::: {.column width="70%"}
**No of main ANSPs ** 
::::::

:::::: {.column width="30%"}
`r main_ansp`
::::::
:::::

::::: columns
:::::: {.column width="70%"}
**No of other ANSPs **
::::::

:::::: {.column width="30%"}
`r other_ansp`
::::::
:::::

::::: columns
:::::: {.column width="70%"}
**No of MET Providers **
::::::

:::::: {.column width="30%"}
`r met_ansp`
::::::
:::::

::::
:::


## Main PRB findings - `r toupper(year_folder)`

[placeholder for text]

## Traffic (`r rp_full` area)

::: {#container-mvt}
:::: {#chart-mvt class="mychart"}
```{r chart-mvt}
#| file: R/chart_level1_traffic_mvt.R
#| out.width: "99%"
```
::::

:::: {#concl-mvt}

```{r mvt_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_ifr_movements.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::
:::

::: {#container-su style="clear: both"}

<br>

:::: {#chart-su class="mychart"}
```{r chart-su}
#| file: R/chart_level1_traffic_su.R
#| out.width: "99%"
```
::::

:::: {#concl-su}

```{r tsu_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_service_units.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::
:::

::: {#container-saf style="clear: both"}

<!-- empty line to ensure next heading leaves enough space -->
<div style="height: 1px"></div>

## Safety (`r rp_full` area)
:::: {#chart-saf class="mychart"}
```{r chart-saf}
#| file: R/chart_level1_saf_ses.R
#| out.width: "99%"
```
::::

:::: {#concl-saf}

```{r saf_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_saf.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::
:::

::: {#container-env style="clear: both"}

<!-- empty line to ensure next heading leaves enough space -->
<div style="height: 1px"></div>

## Environment (`r rp_full` area)

:::: {#chart-env class="mychart"}
```{r chart-env-kea, options = (doclevel=c("level1"))}
#| file: R/chart_level1_kea.R
#| out.width: "99%"
```
::::

:::: {#concl-env}

```{r env_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_env.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::
:::

::: {#container-cap style="clear: both"}

## Capacity (`r rp_full` area)
<!-- empty line to ensure next heading leaves enough space -->
<div style="height: 1px"></div>

:::: {#chart-cap class="mychart"}
```{r chart-cap-er, options = (cztype=c("enroute"))}
#| file: R/chart_level1_cap.R
#| out.width: "99%"
```

<br>

```{r chart-cap-trm, options = (cztype=c("terminal"))}
#| file: R/chart_level1_cap.R
#| out.width: "99%"
```
::::

:::: {#concl-cap}

```{r cap_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_cap.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::
:::


::: {#container-cef style="clear: both"}
<!-- empty line to ensure next heading leaves enough space -->
<div style="height: 1px"></div>

## Cost-efficiency (`r rp_full` area)

:::: {#chart-cef class="mychart"}
```{r chart-cef}
#| file: R/chart_level1_cef_er_ses.R
#| out.width: "99%"
```

<br>

```{r chart-cef-trm-1, options = (cz=c("1", "terminal", "level1"))}
#| file: R/chart_level1_cef.R
#| out.width: "99%"
```
::::

:::: {#concl-cef}

```{r cef_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_cef.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::
:::

