```{r chart_cef_er_1, options = (cz=c("1", "enroute", "level1")), include = FALSE}
#| file: R/chart_level1_cef.R
#| out.width: "100%"
```

```{r chart_cef_er_2, options = (cz=c("2", "enroute", "level1")), eval = (params$no_ecz == 2), include = FALSE}
#| file: R/chart_level1_cef.R
#| out.width: "100%"
```

```{r chart_cef_trm_1, options = (cz=c("1", "terminal", "level1")), eval = (params$no_tcz != 0), include = FALSE}
#| file: R/chart_level1_cef.R
#| out.width: "100%"
```

```{r chart_cef_trm_2, options = (cz=c("2", "terminal", "level1")), eval = (params$no_tcz == 2), include = FALSE}
#| file: R/chart_level1_cef.R
#| out.width: "100%"
```

<!-- ## Safety L2-->

<!-- ### Effectiveness of Safety Management (EoSM) (KPI#1) -->
```{r chart_level1_saf_1, include=FALSE, options = (saf_ansp_index = 1)}
#| file: R/chart_level1_saf.R
#| out.width: "100%"
```

```{r chart_level1_saf_2, eval = (no_saf_ansps > 1), include=FALSE, options = (saf_ansp_index = 2)}
#| file: R/chart_level1_saf.R
#| out.width: "100%"
```

```{r chart_level1_saf_3, eval = (no_saf_ansps > 2), include=FALSE, options = (saf_ansp_index = 3)}
#| file: R/chart_level1_saf.R
#| out.width: "100%"
```

```{r chart_level1_saf_4, eval = (no_saf_ansps > 3), include=FALSE, options = (saf_ansp_index = 4)}
#| file: R/chart_level1_saf.R
#| out.width: "100%"
```

<!-- ### Rate of runway incursions (RIs) (PI#1) -->

```{r chart_saf_ri, include=FALSE}
#| file: R/chart_level2_saf_ri.R
#| out.width: "100%"
```

```{r chart_level2_saf_ri_year_report, eval= (params$country != "MUAC"), options = (safindicator=c("ri")), include=FALSE}
#| file: R/chart_level2_saf_ri_smi_year_report.R
#| out.width: "100%"
```

<!-- ### Rate of separation minima infringements (SMIs) (PI#2) -->

```{r chart_saf_smi, include=FALSE}
#| file: R/chart_level2_saf_smi.R
#| out.width: "100%"
```

```{r chart_level2_saf_smi_year_report, options = (safindicator=c("smi")), include=FALSE}
#| file: R/chart_level2_saf_ri_smi_year_report.R
#| out.width: "100%"
```

<!-- ## Environment L2 -->
<!-- ### En route performance -->
<!-- ##### Horizontal flight efficiency of the actual trajectory (KEA) (KPI#1), of the last filed flight plan (KEP) (PI#1) & shortest constrained route (SCR) (PI#2) -->

```{r chart_env_kea_l2, options = (doclevel=c("level2")), include=FALSE}
#| file: R/chart_level1_kea.R
#| out.width: "100%"
```

```{r chart_env_kea_month, include=FALSE}
#| file: R/chart_level2_kea_month.R
#| out.width: "100%"
```

```{r chart_env_kep_scr, include=FALSE}
#| file: R/chart_level2_kep_scr.R
#| out.width: "100%"
```

```{r chart_env_kep_scr_month, include=FALSE}
#| file: R/chart_level2_kep_scr_month.R
#| out.width: "100%"
```

<!-- ### Terminal performance -->
<!-- #### Additional taxi-out time (AXOT) (PI#3) & Arrival Sequencing and Metering Area (ASMA) time (PI#4) -->

```{r chart_axot_apt, include=FALSE}
#| file: R/chart_level2_env_axot_apt.R
#| out.width: "100%"
```

```{r chart_asma_apt, include=FALSE}
#| file: R/chart_level2_env_asma_apt.R
#| out.width: "100%"
```

<!-- #### Share of arrivals applying continuous descent operations (CDOs) (PI#5) -->

<!-- ### Civil-Military dimension  -->

```{r chart_cdr, include=FALSE}
#| file: R/chart_level2_env_cdr.R
#| out.width: "100%"
```

```{r chart_rsa, include=FALSE}
#| file: R/chart_level2_env_rsa.R
#| out.width: "100%"
```

<!-- ## Capacity L2-->
<!-- ### En route performance -->
<!-- ### En route ATFM delay (KPI#1) -->
```{r chart_cap_er_l2, options = (cztype=c("enroute")), include=FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

```{r chart_cap_er_month, options = (cztype=c("enroute")), include=FALSE}
#| file: R/chart_level2_cap_month.R
#| out.width: "100%"
```

<!-- En route perfromance indicators at ACC level (PI#3-4) -->

```{r chart_level2_cap_perc_delay_above, eval=(params$country != "Luxembourg"), include=FALSE}
#| file: R/chart_level2_cap_perc_delay_above.R
#| out.width: "100%"
```


```{r chart_level2_cap_peak_tp, eval=(params$country != "Luxembourg"), include=FALSE}
#| file: R/chart_level2_cap_peak_tp.R
#| out.width: "100%"
```


<!-- #### Other indicators -->
```{r chart_cap_atco, include=FALSE}
#| file: R/chart_level2_cap_atco.R
#| out.width: "100%"
```

```{r chart_cap_atco_acc, include=FALSE}
#| file: R/chart_level2_cap_atco_acc.R
#| out.width: "100%"
```

<!-- ### Terminal performance -->
<!-- #### Arrival ATFM delay (KPI#2) -->
```{r chart_cap_trm_l2, options = (cztype=c("terminal")), eval=(params$no_tcz != 0), include=FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

```{r chart_cap_trm_month, options = (cztype=c("terminal")), eval=(params$no_tcz != 0), include=FALSE}
#| file: R/chart_level2_cap_month.R
#| out.width: "100%"
```

<!-- ## Cost-efficiency  -->

<!-- # End of charts and tables -->

<!-- Level2 text -->
```{r level_2_text}
source(here("R","get_level2_text.R"))
```

<!-- params -->
```{r fetch-data-state, eval=TRUE}
pp_version <- params$pp_version
acc_no <- params$acc_no
acc_list <- params$acc_list
acc1 <- params$acc1
acc2 <- params$acc2
acc3 <- params$acc3
acc4 <- params$acc4
acc5 <- params$acc5
no_apt_big <- params$no_apt_big
no_apt_small <- params$no_apt_small

nat_curr <- params$nat_curr
xrate_ref <- params$xrate_ref
tsu_share <- params$tsu_share
ert_cost_share <- params$ert_cost_share
ert_trm_share <- params$ert_trm_share

main_ansp <- params$main_ansp
other_ansps_str <- params$other_ansps_str
other_met_str <- params$other_met_str

```

```{r yearly_xrates}
# get yearly xrates

xrate <- xrate_ert |> 
  filter(year == year_report & cz_code == ecz_list$ecz_id[1]) |> 
  select(xrate)

xrate_year_report <- if_else(country == "Luxembourg", 1, pull(xrate))

```

```{r cef-level2-headings}
source("R/get_level2_headings.R")
```


# OVERVIEW

## Contextual information
*`r pp_version`*

```{=latex}

\begin{figure}

\footnotesize

\begin{minipage}[t]{0.31\linewidth}
```

**List of ACCs     ** `r acc_no`  
\hspace*{2em} `r acc1` `r ifelse(acc2 != "", "  ", "")`
`r ifelse(acc2 != "", "\\hspace*{2em}", "")` `r acc2` `r ifelse(acc3 != "", "  ", "")`
`r ifelse(acc3 != "", "\\hspace*{2em}", "")` `r acc3` `r ifelse(acc4 != "", "  ", "")`
`r ifelse(acc4 != "", "\\hspace*{2em}", "")` `r acc4` `r ifelse(acc5 != "", "  ", "")`
`r ifelse(acc5 != "", "\\hspace*{2em}", "")` `r paste0(acc5, "  ")` 

\vspace*{1em}
**No of airports in the scope**  
**of the performance plan:**  
\hspace*{2em} • **≥80'K     ** `r no_apt_big`  
\hspace*{2em} • **<80'K     ** `r no_apt_small`

```{=latex}
\end{minipage}%
%
\begin{minipage}[t]{0.38\linewidth}
```

**Exchange rate (1 EUR=)**  
\hspace*{2em} `r paste0(cef_ref_year, ": ", xrate_ref, " ", nat_curr, "  ")` 
\hspace*{2em} `r paste0(year_report, ": ", xrate_year_report, " ", nat_curr, "  ")`

\vspace*{0.5em}**Share of Union-wide:**  
\hspace*{2em} • **traffic (TSUs) `r year_report`  **  `r paste0(tsu_share, "  ")` 
\hspace*{2em} • **en route costs `r year_report` ** `r paste0(ert_cost_share, "  ")` 
**Share en route / terminal**  
**costs `r year_report`                    ** `r paste0(ert_trm_share, "  ")` 

\vspace*{0.5em}**En route charging zone(s)**
```{r ecz_list_string}
ecz_list_string <- paste0(
  fixed('`\\hspace*{2em}`{=tex}'),
  ecz_list$ecz_name[1],
  if_else(is.na(ecz_list$ecz_name[2]), '' ,  paste0(fixed('` \\\\ \\hspace*{2em}`{=tex}'), ecz_list$ecz_name[2])
          )
)
```
`r paste0(ecz_list_string, "  ")` 

**Terminal charging zone(s)**  
```{r tcz_list_string}
tcz_list_string <- if_else(no_tcz == 0, '`\\hspace*{2em}`{=tex} --',
paste0(
  fixed('`\\hspace*{2em}`{=tex}'),
  tcz_list$tcz_name[1],
  if_else(is.na(tcz_list$tcz_name[2]), '' , paste0(fixed('`\\\\ \\hspace*{2em}`{=tex}'), tcz_list$tcz_name[2])
  ),
  if_else(is.na(tcz_list$tcz_name[3]), '' , paste0(fixed('`\\\\ \\hspace*{2em}`{=tex}'), tcz_list$tcz_name[3])
  )
  )
)
```

`r tcz_list_string`

```{=latex}
\end{minipage}%
%
\begin{minipage}[t]{0.31\linewidth}
```

```{r ansp_list_strings}
# this is very convoluted but I couldnt find any other way
other_ansps_list <- str_split(other_ansps_str, "<br/>")[[1]] %>%
  discard(~ .x == "")

other_ansps_str_1 <- reduce(other_ansps_list, ~ paste(.x, .y, sep = fixed('`\\\\`{=tex}\\hspace*{1.2em}')))

other_met_list <- str_split(other_met_str, "<br/>")[[1]] %>%
  discard(~ .x == "")

other_met_str_1 <- reduce(other_met_list, ~ paste(.x, .y, sep = fixed('`\\\\`{=tex}\\hspace*{1.2em}')))

```


**Main ANSP**  
\hspace*{1em} • `r paste0(main_ansp, "  ")`  

\vspace*{1em}**Other ANSPs**
`\begin{flushleft}`{=tex}
\vspace*{-1em}\hspace*{1em} `r paste0(other_ansps_str_1, "  ")` 
`\end{flushleft}`{=tex}

**MET Providers**
`\begin{flushleft}`{=tex}
\vspace*{-1em}\hspace*{1em} `r other_met_str_1`
`\end{flushleft}`{=tex}

```{=latex}
\end{minipage}%

\end{figure}%
```


## Traffic (En route traffic zone)

```{r mvt_conc}
mvt_conc1 <- get_prb_conclusions(prb_findings_file, "traffic_IFR", "Table_Findings_traffic_IFR")
```

```{r chart_level1_traffic_mvt}
#| file: R/chart_level1_traffic_mvt.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r mvt_conc1`

```{r su_conc1}
tsu_conc1 <- get_prb_conclusions(prb_findings_file, "traffic_SUs", "Table_Findings_traffic_TSU")

```

```{r chart_level1_traffic_su}
#| file: R/chart_level1_traffic_su.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r tsu_conc1`

## Safety (Main ANSP)

```{r saf_conc1}
saf_conc1 <- get_prb_conclusions(prb_findings_file, "safety", "Table_Findings_safety")
```

```{r chart_saf_l1, options = (saf_ansp_index = 1)}
#| file: R/chart_level1_saf.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r saf_conc1`

<!-- exception for luxembourg -->
`r if (params$country == "Luxembourg") "::: {.content-hidden}"`

## Environment (Member State)

```{r concl_env}
env_conc1 <- get_prb_conclusions(prb_findings_file, "environment", "Table_Findings_environment")
```

```{r chart_env_kea_l1, options = (doclevel=c("level1"))}
#| file: R/chart_level1_kea.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r env_conc1`

`r if (params$country == "Luxembourg") ":::"`

## Capacity (Member State)

```{r concl_cap}
cap_er_conc1 <-  get_prb_conclusions(prb_findings_file, "ER_capacity", "Table_Findings_ER_capacity")
cap_trm_conc1 <- get_prb_conclusions(prb_findings_file, "TRM_capacity", "Table_Findings_TRM_capacity")

cap_conc1 <- paste0(if_else(cap_er_conc1 == "character(0\n", "", paste0(cap_er_conc1, "\n\n")), if_else(cap_trm_conc1 == "NA" | stringr::str_detect(cap_trm_conc1, "character"), "", cap_trm_conc1))
```

```{r chart_cap_er, options = (cztype=c("enroute")), include = (params$country != "Luxembourg")}
#| file: R/chart_level1_cap.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r if_else(params$country != "Luxembourg", cap_er_conc1, '')`

```{r chart_cap_trm, options = (cztype=c("terminal")), include = params$no_tcz != 0}
#| file: R/chart_level1_cap.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r if_else(params$no_tcz != 0, cap_trm_conc1, '')`

## Cost-efficiency (En route/Terminal charging zone(s))

```{r concl-cef}
cef_conc1 <- get_prb_conclusions(prb_findings_file, "cost-efficiency", "Table_Findings_CEFF")
```

`r if ((params$no_ecz + params$no_tcz) >1) ":::: {.content-hidden}"`
```{=latex}
\begin{figure}[H]
\centering
\includegraphics[width=0.52\linewidth,height=\textheight,keepaspectratio]{index_files/figure-pdf/chart_cef_er_1-1.pdf}
\end{figure}
```
`r if ((params$no_ecz + params$no_tcz) >1) "::::"`


`r if ((params$no_ecz + params$no_tcz) == 1) ":::: {.content-hidden}"`
`r layout_2fig("chart_cef_er_1", if_else(params$no_ecz == 1, "chart_cef_trm_1", "chart_cef_er_2"))`
`r if ((params$no_ecz + params$no_tcz) == 1) "::::"`


`r if ((params$no_ecz + params$no_tcz) != 3 | params$no_ecz == 1) ":::: {.content-hidden}"`
```{=latex}
\begin{figure}[H]
\centering
\includegraphics[width=0.52\linewidth,height=\textheight,keepaspectratio]{index_files/figure-pdf/chart_cef_trm_1-1.pdf}
\end{figure}
```

`r if ((params$no_ecz + params$no_tcz) != 3 | params$no_ecz == 1) "::::"`


`r if ((params$no_ecz + params$no_tcz) != 3 | params$no_ecz == 2) ":::: {.content-hidden}"`
```{=latex}
\begin{figure}[H]
\centering
\includegraphics[width=0.52\linewidth,height=\textheight,keepaspectratio]{index_files/figure-pdf/chart_cef_trm_2-1.pdf}
\end{figure}
```

`r if ((params$no_ecz + params$no_tcz != 3) | params$no_ecz == 2) "::::"`

`r cef_conc1`

`r if (year_folder == params$rp_summary_year) "::: {.content-hidden}"`

# SAFETY - `r toupper(params$country)`

## PRB monitoring

`r saf_conc1`

\needspace{2\baselineskip}

## Effectiveness of Safety Management (EoSM) (KPI#1)

`r if (params$no_saf_ansps >1) ":::: {.content-hidden}"`
```{=latex}
\begin{figure}[H]
\centering
\includegraphics[width=0.52\linewidth,height=\textheight,keepaspectratio]{index_files/figure-pdf/chart_level1_saf_1-1.pdf}
\end{figure}
```
`r if (params$no_saf_ansps >1) "::::"`


`r if (params$no_saf_ansps == 1) ":::: {.content-hidden}"`
`r layout_2fig("chart_level1_saf_1", if_else(params$no_saf_ansps == 1, "chart_level1_saf_1", "chart_level1_saf_2"))`
`r if (params$no_saf_ansps == 1) "::::"`


`r if (params$no_saf_ansps != 3) ":::: {.content-hidden}"`
```{=latex}
\begin{figure}[H]
\centering
\includegraphics[width=0.52\linewidth,height=\textheight,keepaspectratio]{index_files/figure-pdf/chart_level1_saf_3-1.pdf}
\end{figure}
```

`r if (params$no_saf_ansps != 3) "::::"`


`r if (params$no_saf_ansps != 4) ":::: {.content-hidden}"`
`r layout_2fig(if_else(params$no_saf_ansps < 3, "chart_level1_saf_1", "chart_level1_saf_3"), if_else(params$no_saf_ansps < 4, "chart_level1_saf_1", "chart_level1_saf_4"))`
`r if (params$no_saf_ansps != 4) "::::"`

\needspace{3\baselineskip}


\biggertext{Focus on EoSM}

```{r results = "asis"}
cat(quarto_paragraph_breaks(saf_eosm_text))
```

`r if (params$country == "MUAC") "::: {.content-hidden}"`

\needspace{2\baselineskip}

## Safety occurrences

### Rate of runway incursions (RIs) (PI#1)

`r layout_2fig("chart_saf_ri", "chart_level2_saf_ri_year_report")`

```{r table_level2_saf_ri_apt, eval= (params$country != "MUAC")}
#| file: R/table_level2_saf_ri_apt.R
#| include: false
```

``` {r, eval= (params$country != "MUAC")}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table(
  title = paste0("Rate of RIs per 100,000 airport movements - ",  country),
  df = data_prep,
  col_align = "clrrr",
  col_widths = c(6, 27, 67/3, 67/3, 67/3),
  paginate = (country == "France")
))
```

`r if (params$country == "MUAC") ":::"`

\needspace{3\baselineskip}


\biggertext{Focus on runway incursions}

```{r results = "asis"}
cat(quarto_paragraph_breaks(saf_ri_text))

```

\needspace{2\baselineskip}

### Rate of separation minima infringements (SMIs) (PI#2)

`r layout_2fig("chart_saf_smi", "chart_level2_saf_smi_year_report")`


```{r table_level2_saf_smi_ansp_pdf1, eval=(year_folder != params$rp_summary_year)}
#| file: R/table_level2_saf_smi_ansp_pdf1.R
#| include: false
```


``` {r table_level2_saf_smi_ansp_pdf1-p, eval=(year_folder != params$rp_summary_year)}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table_2level(
  title = paste0("Rate of SMI with ANS contribution per 100,000 flight hours"),
  df = data_prep,
  col_align = "llrrrrrrrrrr",
  col_widths = c(3,12,rep(8.5,10)),
  body_fontsize = c(8, 10),
  cell_pad_em = 0.3,
  wrap_raw_block = FALSE,
  header_row_height_ex = 2.4,
  row_extrarowheight_pt = 2 
))
```

\vspace{-20pt}

```{r table_level2_saf_smi_ansp_pdf2, eval=(year_folder != params$rp_summary_year)}
#| file: R/table_level2_saf_smi_ansp_pdf2.R
#| include: false
```

``` {r table_level2_saf_smi_ansp_pdf2_p, eval=(year_folder != params$rp_summary_year)}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table_2level(
  title = NA,
  df = data_prep,
  col_align = "llrrrrrrrrrr",
  col_widths = c(3,12,rep(8.5,10)),
  body_fontsize = c(8, 10),
  cell_pad_em = 0.3,
  wrap_raw_block = FALSE,
  header_row_height_ex = 2.4,
  row_extrarowheight_pt = 2 
  
))
```

\needspace{3\baselineskip}


\biggertext{Focus on separation minima}

```{r results = "asis"}
cat(quarto_paragraph_breaks(saf_smi_text))

```

\needspace{2\baselineskip}

### Quality of occurences reporting 

```{r results = "asis"}
cat(quarto_paragraph_breaks(saf_qr_text))

```

\needspace{2\baselineskip}

# ENVIRONMENT - `r toupper(params$country)`

## PRB monitoring

`r env_conc1`

`r if (params$country == "Luxembourg") "::: {.content-hidden}"`

\needspace{3\baselineskip}

## En route performance

### Horizontal flight efficiency of the actual trajectory (KEA) (KPI#1), of the last filed flight plan (KEP) (PI#1) , shortest constrained route (SCR) (PI#2) and vertical flight efficiency of the actual trajectory (PI#3)


`r layout_2fig("chart_env_kea_l2", "chart_env_kea_month")`

`r layout_2fig("chart_env_kep_scr", "chart_env_kep_scr_month")`

```{r chart_vfe, eval=(params$country != "Luxembourg")}
#| file: R/chart_level2_env_vfe_ert.R
#| out.width: "50%"
#| fig.align: "center"
#| fig-pos: "H"
```

\needspace{3\baselineskip}

`\biggertext{Focus on en route performance}`{=latex}

**KEA**

```{r env_er_text_kea}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_er_kea.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_er_kea.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_er_nsa_titles_kea)

``` 

**KEP**

```{r env_er_text_kep}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_er_kep.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_er_kep.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_er_nsa_titles_kep)

``` 

**KES**

```{r env_er_text_kes}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_er_kes.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_er_kes.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_er_nsa_titles_kes)

``` 

**Vertical flight efficiency**

```{r env_er_text_vfe}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_er_vfe.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_er_vfe.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_er_nsa_titles_vfe)

``` 



`r if (params$country == "Luxembourg") ":::"`


`r if (params$no_tcz == 0) "::: {.content-hidden}"`

\needspace{3\baselineskip}

## Terminal performance

### Additional taxi-out time (AXOT) (PI#4), Additional taxi-in time (AXIT) (PI#5) & Arrival Sequencing and Metering Area (ASMA) time (PI#6)

```{r chart_axot_asma_country, eval=(year_folder != params$rp_summary_year)}
#| file: R/chart_level2_env_axot_asma_country.R
#| out.width: "50%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r layout_2fig("chart_axot_apt", "chart_asma_apt")`

\needspace{3\baselineskip}

`\biggertext{Focus on AXOT, AXIT \& ASMA}`{=latex}

**AXOT**

```{r env_trm_text_axot, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_trm_axot.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_trm_axot.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_trm_nsa_titles_axot)

``` 

**AXIT**

```{r env_trm_text_axit, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_trm_axit.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_trm_axit.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_trm_nsa_titles_axit)

``` 

**ASMA**

```{r env_trm_text_asma, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_trm_asma.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_trm_asma.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_trm_nsa_titles_asma)

``` 


```{r table_level2_env_apt_pis, eval=!(params$no_tcz == 0 | params$country == params$rp_full)}
#| file: R/table_level2_env_apt_pis.R
#| include: false
```


``` {r, eval=!(params$no_tcz == 0 | params$country == params$rp_full), include=(!(params$no_tcz == 0 | params$country == params$rp_full))}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table_2level(
  title = paste0("Airport level"),
  df = data_prep_pdf,    
  caption_fontsize = c(10, 10),
  body_fontsize = c(8, 9.6),
  col_align = "lrrrrrrrrrrrrrrr",
  col_widths = c(10,rep(90/15,15)),
  wrap_raw_block = FALSE,
  header_row_height_ex = 2.4,
  row_extrarowheight_pt = 2,
  paginate = (country == "France") 
))
```


###  Average duration in climb (PI#7) and descent (PI#8)

```{r chart-cdo-apt-param, eval = (params$no_tcz > 0), include=FALSE}
#| file: R/chart_level2_env_cdo_apt.R
#| out.width: "100%"

```

```{r cdo-airports-check}
if(!exists("cdo_airports")) {cdo_airports <-0}
```


```{r chart-cdo-apt, eval=((year_folder != params$rp_summary_year) & (params$no_tcz > 0) & cdo_airports <= 6)}
#| file: R/chart_level2_env_cdo_apt.R
#| out.width: "60%"
#| fig.align: "center"
#| fig-pos: "H"
```

```{r chart-cdo-apt-big, eval=((year_folder != params$rp_summary_year) & (params$no_tcz > 0) & cdo_airports > 6)}
#| file: R/chart_level2_env_cdo_apt.R
#| out.width: "100%"
#| fig.align: "center"
#| fig-pos: "H"
```

\needspace{2\baselineskip}

`\biggertext{Focus on average duration in descent and climb}`{=latex}

**Average duration in descent**

```{r env_trm_text_vfed, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_trm_vfed.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_trm_vfed.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_trm_nsa_titles_vfed)

``` 

**Average duration in climb**


```{r env_trm_text_vfec, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_trm_vfec.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_trm_vfec.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_trm_nsa_titles_vfec)

``` 


```{r table_level2_env_apt_pis_cdco, eval=!(params$no_tcz == 0 | params$country == params$rp_full)}
#| file: R/table_level2_env_apt_pis_cdco.R
#| include: false
```


``` {r, eval=!(params$no_tcz == 0 | params$country == params$rp_full), include=(!(params$no_tcz == 0 | params$country == params$rp_full))}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table_2level(
  title = paste0("Airport level"),
  df = data_prep_pdf,    
  caption_fontsize = c(10, 10),
  body_fontsize = c(8, 9.6),
  col_align = "lrrrrrrrrrr",
  col_widths = c(20,rep(80/10,10)),
  wrap_raw_block = FALSE,
  header_row_height_ex = 2.4,
  row_extrarowheight_pt = 2,
  paginate = (country == "France") 
))
```


`r if (params$no_tcz == 0) ":::"`


`r if (params$country == "Luxembourg") "::: {.content-hidden}"`

## Civil-Military dimension

```{r chart_ersa}
#| file: R/chart_level2_env_ersa.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

`r layout_2fig("chart_cdr", "chart_rsa")`

\needspace{3\baselineskip}

`\biggertext{Focus on Civil-Military dimension}`{=latex}

**Effective use of reserved or segregated local airspace**

```{r env_mil_text_ersa}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_mil_ersa.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_mil_ersa.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_mil_nsa_titles_ersa)

``` 

**Rate of planning via available airspace structures**

```{r env_mil_text_rap}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_mil_rap.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_mil_rap.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_mil_nsa_titles_rap)

``` 

**Rate of using available airspace structures**

```{r env_mil_nsa_rau}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_env_mil_rau.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_env_mil_rau.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, env_mil_nsa_titles_rau)

``` 

`r if (params$country == "Luxembourg") ":::"`

# CAPACITY - `r toupper(params$country)`

## PRB monitoring

```{r cap-prb}
if (params$country == "Luxembourg") {
  cap_er_conc1 <- ""
  } else {
  cap_er_conc1 <- get_prb_conclusions(prb_findings_file, "ER_capacity", "Table_Findings_ER_capacity")
}
```

`r cap_er_conc1`

`r if (params$no_tcz == 0) "::: {.content-hidden}"`

```{r cap-trm-prb}
cap_trm_conc1 <- get_prb_conclusions(prb_findings_file, "TRM_capacity", "Table_Findings_TRM_capacity")

cap_trm_conc1 <- if_else(cap_trm_conc1 == "NA" | stringr::str_detect(cap_trm_conc1, "character"), "", cap_trm_conc1)
```

`r cap_trm_conc1`

`r if (params$no_tcz == 0) ":::"`



`r if (params$country == "Luxembourg") "::: {.content-hidden}"`

\needspace{3\baselineskip}

## En route performance

### En route ATFM delay (KPI#1)

`r layout_2fig("chart_cap_er_l2", "chart_cap_er_month")`

```{r chart_cap_delay_bin, eval=(year_folder != params$rp_summary_year)}
#| file: R/chart_level2_cap_delay_bin.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

\needspace{3\baselineskip}

\biggertext{Focus on en route ATFM delay}

**En route ATFM delay**

```{r cap_er_text_atfm, eval=(params$no_ecz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_er_atfm.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_cap_er_atfm.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, cap_er_nsa_titles_atfm)

``` 

**En route capacity incentive scheme**
```{r cap_er_text_incentive, eval=(params$no_ecz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_er_incentive.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 



### En route performance indicators at ACC level (PI#3-4)

`r layout_2fig("chart_level2_cap_perc_delay_above", "chart_level2_cap_peak_tp")`

\needspace{3\baselineskip}

`\biggertext{Focus en route performance indicators at ACC level}`{=latex}

**Percentage of total en route ATFM delay that occurred on days when the daily throughput was above the expected daily traffic**

```{r cap_ert_text_above}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_er_above.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_cap_er_above.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, cap_er_nsa_titles_above)

``` 

**Annual weighted average of the daily peak throughput**

```{r cap_ert_text_tput}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_er_tput.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_cap_er_tput.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, cap_er_nsa_titles_tput)

``` 


### Other indicators

`r layout_2fig("chart_cap_atco", "chart_cap_atco_acc")`

```{r chart_cap_sector_opening, eval=(year_folder != params$rp_summary_year)}
#| file: R/chart_level2_cap_sector_opening.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

\needspace{3\baselineskip}

`\biggertext{Focus on ATCOs in operations}`{=latex}

```{r cap_ert_text_atco}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_er_atco.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_cap_er_atco.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, cap_er_nsa_titles_atco)

``` 



`r if (params$country == "Luxembourg") ":::"`


`r if (params$no_tcz == 0) "::: {.content-hidden}"`


\needspace{3\baselineskip}

## Terminal performance

### Arrival ATFM delay (KPI#2)

`r layout_2fig("chart_cap_trm_l2", "chart_cap_trm_month")`

\needspace{3\baselineskip}

`\biggertext{Focus on arrival ATFM delay}`{=latex}

**Arrival ATFM delay**

```{r cap_trm_text_atfm, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_trm_atfm.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_cap_trm_atfm.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, cap_trm_nsa_titles_atfm)

``` 

**Terminal capacity incentive scheme**
```{r cap_trm_text_incentive, eval=(params$no_ecz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_trm_incentive.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 



### Other terminal performance indicators (PI#1-3)

```{r chart_cap_all_causes_delay, eval=(year_folder != params$rp_summary_year)}
#| file: R/chart_level2_cap_all_causes_delay.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

```{r table_level2_cap_apt_pis_pdf1, eval=(params$no_tcz != 0)}
#| file: R/table_level2_cap_apt_pis_pdf1.R
#| include: false
```


``` {r eval=(params$no_tcz != 0), include=(params$no_tcz != 0)}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table_2level(
  title = paste0("Airport level"),
  df = data_prep,
  body_fontsize = c(9, 11),
  col_align = "lrrrrrrrrrr",
  col_widths = c(20,rep(7,5), rep(9,5)),
  wrap_raw_block = FALSE,
  header_row_height_ex = 2.4,
  row_extrarowheight_pt = 2,
  paginate = (country == "France") 
))
```

\vspace{-20pt}

```{r table_level2_cap_apt_pis_pdf2, eval=(params$no_tcz != 0)}
#| file: R/table_level2_cap_apt_pis_pdf2.R
#| include: false
```


``` {r eval=(params$no_tcz != 0), include=(params$no_tcz != 0)}
#| echo: false
#| results: asis
 
cat(make_quarto_latex_table_2level(
  title = NA,
  df = data_prep,
  col_align = "lrrrrrrrrrr",
  body_fontsize = c(9, 11),
  col_widths = c(20,rep(8,10)),
  wrap_raw_block = FALSE,
  header_row_height_ex = 2.4,
  row_extrarowheight_pt = 2,
  paginate = (country == "France") 
))
```


\needspace{3\baselineskip}

`\biggertext{Focus on performance indicators at airport level}`{=latex}

**ATFM slot adherence**

```{r cap_trm_text_slot, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_trm_slot.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_cap_trm_slot.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, cap_trm_nsa_titles_slot)

``` 

**ATC pre-departure delay**

```{r cap_trm_text_pddelay, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_trm_pddelay.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_cap_trm_pddelay.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, cap_trm_nsa_titles_pddelay)

``` 

**All causes pre-departure delay**

```{r cap_trm_text_acdelay, eval=(params$no_tcz != 0)}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_pru_cap_trm_acdelay.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))


path <- sprintf("./qmd_parts/%s/%s/_%s_%s_nsa_cap_trm_acdelay.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, cap_trm_nsa_titles_acdelay)

``` 


`r if (params$no_tcz == 0) ":::"`

# COST-EFFICIENCY - `r toupper(params$country)`

## PRB monitoring

```{r concl_cef_duc_e1}
cef_conc1 <- get_prb_conclusions(prb_findings_file, "cost-efficiency", "Table_Findings_CEFF")
```

`r cef_conc1`


```{r generate_ceff_er sections}
#| echo: false
#| results: asis

myn <- params$no_ecz
myn <- if (is.na(myn) || myn < 1) 0L else as.integer(myn)

for (i in seq_len(myn)) {
  f <- sprintf("_cost-efficiency-er%d-1.qmd", i)

  if (!file.exists(f)) {
    cat(sprintf("\n\n**Missing include file:** `%s`\n\n", f))
    next
  }

  # Execute the child document and inject its rendered output
  cat(knitr::knit_child(f, quiet = TRUE), sep = "\n")
  cat("\n\n")
}
```

```{r generate_ceff_trm sections}
#| echo: false
#| results: asis

myn <- params$no_tcz
myn <- if (is.na(myn) || myn < 1) 0L else as.integer(myn)

for (i in seq_len(myn)) {
  f <- sprintf("_cost-efficiency-tz%d-1.qmd", i)

  if (!file.exists(f)) {
    cat(sprintf("\n\n**Missing include file:** `%s`\n\n", f))
    next
  }

  # Execute the child document and inject its rendered output
  cat(knitr::knit_child(f, quiet = TRUE), sep = "\n")
  cat("\n\n")
}
```
