```{r saf_level2_text}
# get yearly xrates

xrate <- xrate_ert %>% 
  filter(year == year_report, cz_code == ecz_list$ecz_id[1] ) |> 
  select(xrate)

xrate_year_report <- if_else(country == "Luxembourg", 1, pull(xrate))

```

::: {.grid .align-items-center}
:::: {.g-col-9}
[Annual Monitoring Report `r toupper(params$year_folder)` - {{< var doc.country >}}]{.fakeh1}
::::

:::: {.g-col-3}
<span class="no-external-icon">[<i class="fa fa-download"></i> Download Report](`r params$home_address`/download/{{< var doc.year_report >}}/PRB-Annual-Monitoring-Report_{{< var doc.country >}}_{{< var doc.year_report >}}.pdf){.btn .btn-light .text-dark .border .bg-secondary-subtle .rounded}</span>
::::
:::


## Contextual information
*`r pp_version`*

<!-- ******************* 1st column -->
::: columns
:::: {.column width="30%"}
::::: columns
:::::: {.column width="50%"}
**List of ACCs  ** `r acc_no`
::::::

:::::: {.column width="50%"}
`r acc1`<br/>`r acc2`<br/>`r acc3`<br/>`r acc4`<br/>`r acc5`
::::::
:::::

::::: columns
:::::: {.column width="50%"}
**No of airports in the scope of the performance plan**
::::::

:::::: {.column width="50%"}
**≥80'K    ** `r no_apt_big`<br/> **<80'K     ** `r no_apt_small`
::::::
:::::
::::

<!-- ******************* 2nd column -->
:::: {.column width="38%"}

`r if (params$year_folder == params$rp_summary_year) ":::: {.content-hidden}"`
::::: columns
:::::: {.column width="50%"}
**Exchange rate (1 EUR=) **
::::::
`r if (params$year_folder == params$rp_summary_year) "::::"`

:::::: {.column width="50%"}
`r paste0(cef_ref_year, ": ", xrate_ref, " ", nat_curr)`\
`r paste0(year_report, ": ", xrate_year_report, " ", nat_curr)`
::::::
:::::

<p style="margin-bottom: 0.5rem"> **Share of Union-wide traffic (TSUs) `r toupper(params$year_folder)` **  `r tsu_share` </p>

<p style="margin-bottom: 0.5rem"> **Share of Union-wide en route costs `r toupper(params$year_folder)` ** `r ert_cost_share` </p>

**Share en route / terminal costs `r toupper(params$year_folder)` ** `r ert_trm_share`

::::: columns
:::::: {.column width="50%"}
<p style="margin-bottom: 0.5rem">**En route charging zone(s)**</p>
::::::

:::::: {.column width="50%"}
```{r}
ecz_list_string <- paste0(
  ecz_list$ecz_name[1],
  if_else(is.na(ecz_list$ecz_name[2]) == TRUE, '' ,  paste0('<br/>', ecz_list$ecz_name[2]))
)
```

<p style="margin-bottom: 0.5rem">`r ecz_list_string`</p>

::::::
:::::

::::: columns
:::::: {.column width="50%"}
[**Terminal charging zone(s)**]{.context-text}
::::::

:::::: {.column width="50%"}
```{r}
tcz_list_string <- if_else(no_tcz == 0, '',
                           paste0(tcz_list$tcz_name[1], 
                                  if_else(is.na(tcz_list$tcz_name[2]) == TRUE, '' ,  
                                          paste0('<br/>', tcz_list$tcz_name[2])
                                          ),
                                  if_else(is.na(tcz_list$tcz_name[3]) == TRUE, '' ,  
                                          paste0('<br/>', tcz_list$tcz_name[3])
                                          )
                                  )
                           )
```

`r tcz_list_string`

::::::
:::::
::::

<!-- ******************* 3rd column -->
:::: {.column width="32%"}
::::: columns
:::::: {.column width="30%"}
**Main ANSP ** 
::::::

:::::: {.column width="70%"}
• `r main_ansp`
::::::
:::::

::::: columns
:::::: {.column width="30%"}
**Other ANSPs **
::::::

:::::: {.column width="70%"}
`r other_ansps_str`
::::::
:::::

::::: columns
:::::: {.column width="30%"}
**MET Providers **
::::::

:::::: {.column width="70%"}
`r other_met_str`
::::::
:::::

::::
:::

## Traffic (En route traffic zone)

::: {#container-mvt}
:::: {#chart-mvt class="mychart"}
```{r chart-mvt}
#| file: R/chart_level1_traffic_mvt.R
#| out.width: "99%"
```
::::

:::: {#concl-mvt}

```{r mvt_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_ifr_movements.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::
:::

::: {#container-su style="clear: both"}

<br>

:::: {#chart-su class="mychart"}
```{r chart-su}
#| file: R/chart_level1_traffic_su.R
#| out.width: "99%"
```
::::

:::: {#concl-su}

```{r tsu_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_service_units.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::
:::

::: {#container-saf style="clear: both"}
<!-- empty line to ensure next heading leaves enough space -->
<div style="height: 1px"></div>

## Safety (Main ANSP)

```{r chart_saf_eosm}
#| out.width: "99%"
#| echo: false

source("R/chart_level1_saf.R")
```

:::: {#chart-saf class="mychart"}
```{r chart-saf}
#| echo: false
mycharts[[1]]
```
::::

:::: {#concl-saf}

```{r saf_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_saf.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::
:::

<!-- empty line to ensure next heading leaves enough space -->
<div style="height: 1px"></div>

`r if (params$country == "Luxembourg") "::: {.content-hidden}"`
::: {#container-env style="clear: both"}

## Environment (Member State)

:::: {#chart-env class="mychart"}
```{r chart-env-kea, options = (doclevel=c("level1"))}
#| file: R/chart_level1_kea.R
#| out.width: "99%"
```
::::

:::: {#concl-env}

```{r env_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_env.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::
:::
`r if (params$country == "Luxembourg") ":::"`


::: {#container-cap style="clear: both"}

## Capacity (Member State)
<!-- empty line to ensure next heading leaves enough space -->
<!-- <div style="height: 1px"></div> -->

:::: {#chart-cap class="mychart"}
`r if (params$country == "Luxembourg") "::::: {.content-hidden}"`
```{r chart-cap-er, options = (cztype=c("enroute"))}
#| file: R/chart_level1_cap.R
#| out.width: "99%"
```

<br>

`r if (params$country == "Luxembourg") ":::::"`


`r if (params$no_tcz == 0) "::::: {.content-hidden}"`

```{r chart-cap-trm, options = (cztype=c("terminal"))}
#| file: R/chart_level1_cap.R
#| out.width: "99%"
```

`r if (params$no_tcz == 0) ":::::"`
::::

:::: {#concl-cap}

```{r cap_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_cap.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::
:::

::: {#container-cef style="clear: both"}
<!-- empty line to ensure next heading leaves enough space -->
<div style="height: 1px"></div>

## Cost-efficiency (En route/Terminal charging zone(s))

:::: {#chart-cef-1 class="mychart"}
```{r chart-cef-er-1, options = (cz=c("1", "enroute", "level1"))}
#| file: R/chart_level1_cef.R
#| out.width: "99%"
```

<br>

`r if (params$no_ecz < 2) "::::: {.content-hidden}"`

```{r chart-cef-er-2, options = (cz=c("2", "enroute", "level1"))}
#| file: R/chart_level1_cef.R
#| out.width: "99%"
```

`r if (params$no_ecz < 2) ":::::"`


`r if (params$no_tcz == 0) "::::: {.content-hidden}"`
<br>

```{r chart-cef-trm-1, options = (cz=c("1", "terminal", "level1"))}
#| file: R/chart_level1_cef.R
#| out.width: "99%"
```

`r if (params$no_tcz == 1) ":::::: {.content-hidden}"`
<br>

```{r chart-cef-trm-2, options = (cz=c("2", "terminal", "level1"))}
#| file: R/chart_level1_cef.R
#| out.width: "99%"
```

`r if (params$no_tcz == 1) "::::::"`

`r if (params$no_tcz < 3) ":::::: {.content-hidden}"`
<br>

```{r chart-cef-trm-3, options = (cz=c("3", "terminal", "level1"))}
#| file: R/chart_level1_cef.R
#| out.width: "99%"
```

`r if (params$no_tcz < 3) "::::::"`


`r if (params$no_tcz == 0) ":::::"`
::::

:::: {#concl-cef}

```{r cef_prb}
#| echo: false
#| output: asis

path <- sprintf("./qmd_parts/%s/%s/_%s_%s_prb_cef.qmd", as.character(year_report),country,country, as.character(year_report))

replace_headings(path, character(0))

``` 

::::
:::