```{r saf-level2-text}
# define ranges and import data
if (params$country == "SES RP3") {
  saf_text <- ""
  
} else {
  sheet <- country
  
  range <- "A15:G30"
  saf_all <- read_range(saf_eosm_file, sheet, range) 
  saf_all <- saf_all |> 
      rename(a = 1) 
  
  # replace NAs by empty strings
  saf_all[is.na(saf_all)] <- ""
  
  #define titles to lookup
  saf_titles <- c("Observations",
                  "**Observations**"
  )
  
  saf_heading_positions <- which(saf_all$a %in% saf_titles)
  
  saf_text <- saf_all[(saf_heading_positions[1]+1):(saf_heading_positions[1]+1), 1]
}

```
::: {.grid .align-items-center}
:::: {.g-col-9}
[Safety - {{< var doc.country >}}]{.fakeh1}
::::

:::: {.g-col-3}
<!-- <span class="no-external-icon">[<i class="fa fa-download"></i> Download Report](`r params$home_address`/download/{{< var doc.year_report >}}/PRB-Annual-Monitoring-Report_{{< var doc.country >}}_{{< var doc.year_report >}}.pdf){.btn .btn-light .text-dark .border .bg-secondary-subtle .rounded} -->
<!-- </span> -->
::::
:::


## PRB monitoring
```{r concl-saf}
saf_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "safety", "Table_Findings_safety")
```

`r saf_conc1`

::: {#container-saf-indicators}

`r if_else(params$country == "SES RP3", "## Actual versus planned number of ANSPs achieving the level of the EoSM targets for RP3 ahead of 2024", "## Effectiveness of Safety Management (EoSM) (KPI#1)")`

:::: {layout="[ 20, 60, 20 ]"}

::::: {#empty-div}
:::::

::::: {.chart-container}  
`r if (params$country != "SES RP3") "::::: {.content-hidden}"`
```{r chart-saf-ansp}
#| file: R/chart_level1_saf_ses.R
#| out.width: "100%"
```
`r if (params$country != "SES RP3") ":::::"`

`r if (params$country == "SES RP3") "::::: {.content-hidden}"`
```{r chart-saf-eosm}
#| file: R/chart_level1_saf.R
#| out.width: "100%"
```
`r if (params$country == "SES RP3") ":::::"`
:::::
::::

`r if (params$country == "SES RP3") ":::: {.content-hidden}"`
:::: {.callout-note collapse=true}

#### Focus on EoSM

`r saf_text`

::::
`r if (params$country == "SES RP3") "::::"`


`r if (params$country == "MUAC") ":::: {.content-hidden}"`

## Occurrences - Rate of runway incursions (RIs) (PI#1) & Rate of separation minima infringements (SMIs) (PI#2)

:::: {layout="[ 50, 50 ]"}
::::: {.chart-container}  
```{r chart_saf_ri}
#| file: R/chart_level2_saf_ri.R
#| out.width: "100%"
```
:::::

::::: {.chart-container}  
```{r chart_saf_smi}
#| file: R/chart_level2_saf_smi.R
#| out.width: "100%"
```
:::::

::::

`r if (params$country == "MUAC") "::::"`

:::





