# Annual Monitoring Report {{< var doc.year_report >}} - SES RP3

## Overview

### Contextual information
```{r fetch-data-ses, eval=TRUE}
data_context <-read_xlsx(
  paste0(data_folder, "SES file.xlsx"),
  sheet = "Context",
  range = cell_limits(c(1, 1), c(NA, NA))) %>%
  as_tibble() %>% 
  clean_names() %>% 
  filter(year_report == .env$year_report & year == .env$year_report)

acc_no_context <- data_context %>% select(number_of_acc) %>% pull()
no_apt_big_context <- data_context %>% select(no_apts_big) %>% pull()
no_apt_small_context <- data_context %>% select(no_apts_small) %>% pull()

ert_trm_share_context <- data_context %>% select(ert_trm_share) %>% pull()
ert_cz_context <- data_context %>% select(ert_cz) %>% pull()
trm_cz_context <- data_context %>% select(trm_cz) %>% pull()

main_ansp_context <- data_context %>% select(main_ans_ps_ert) %>% pull()
other_ansp_context <- data_context %>% select(other_ans_ps_ert) %>% pull()
met_ansp_context <- data_context %>% select(met_providers) %>% pull()
```

::: {layout="[ 34, 38, 28 ]"}

::::{#1st-column}
**No of ACCs   ** `r acc_no_context`  
```{=tex}
\par\vspace{1em}
```

**No of airports in the scope**
```{=tex}
```
**of the performance plan:**

- **≥80'K     ** `r no_apt_big_context`
- **<80'K     ** `r no_apt_small_context`

::::

::::{#2nd-column}
```{=tex}
\vspace*{-\baselineskip} % Adjust vertical alignment to the top
```
**Share en route / terminal**
```{=tex}
```
**costs `r year_report`                 ** `r ert_trm_share_context`
```{=tex}
\par\vspace{1em}
```
**En route charging zone(s)     ** `r ert_cz_context`
```{=tex}
\par\vspace{1em}
```
**Terminal charging zone(s)    ** `r trm_cz_context`
::::

::::{#3rd-column}
```{=tex}
\vspace*{-\baselineskip} % Adjust vertical alignment to the top
\vspace{-1.5em}
```
**No of main ANSPs     ** `r main_ansp_context`
```{=tex}
\par\vspace{1em}
```
**No of other ANSPs    ** `r other_ansp_context`
```{=tex}
\par\vspace{1em}
```
**No of MET Providers ** `r met_ansp_context`
::::

:::

### Main PRB findings - {{< var doc.year_report >}}

```{r main-concl}
main_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "main", "Table_Findings_main")
```

`r main_conc1`

### Traffic (SES RP3 area)
<!-- https://tex.stackexchange.com/questions/215442/is-there-a-way-to-set-a-parbox-to-a-minimum-height -->

```{=tex}
\setlength{\fboxrule}{0pt} % Set the border width to 0pt (no border)
\setlength{\fboxsep}{0pt} % Remove padding
\sbox{0}{\parbox{1\textwidth}{

\begin{wrapfigure}[12]{l}{0.5\linewidth}
\vspace{-15pt}
```

```{r chart-level1-traffic-mvt}
#| file: R/chart_level1_traffic_mvt.R
#| out.width: "100%"
```

```{=tex}
\end{wrapfigure}
\setlength\parskip{1em plus 0.8em} % Space between paragraphs
```

```{r mvt-conc1}
mvt_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "traffic_IFR", "Table_Findings_traffic_IFR")
```

`r mvt_conc1`

```{=tex}
}}
\ifdim\dimexpr\ht0+\dp0<7.0cm 
\dp0\dimexpr7.0cm-\ht0\fi

\fbox{\usebox{0}}
```

```{=tex}
\vspace{10pt}
\sbox{0}{\parbox{1\textwidth}{

\begin{wrapfigure}[12]{l}{0.5\linewidth}
\vspace{-15pt}
```

```{r chart-level1-traffic-su}
#| file: R/chart_level1_traffic_su.R
#| out.width: "100%"
```

```{=tex}
\end{wrapfigure}
\setlength\parskip{1em plus 0.8em} % Space between paragraphs
```

```{r}
tsu_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "traffic_SUs", "Table_Findings_traffic_TSU")
```

`r tsu_conc1`

```{=tex}
}}
\ifdim\dimexpr\ht0+\dp0<7.0cm 
\dp0\dimexpr7.0cm-\ht0\fi

\fbox{\usebox{0}}
```


### Safety (SES RP3 area)

```{=tex}
\sbox{0}{\parbox{1\textwidth}{

\begin{wrapfigure}[13]{l}{0.5\linewidth}
\vspace{-15pt}
```

```{r chart-level1-saf-ses}
#| file: R/chart_level1_saf_ses.R
#| out.width: "100%"
```

```{=tex}
\end{wrapfigure}
\setlength\parskip{1em plus 0.8em} % Space between paragraphs
```

```{r}
saf_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "safety", "Table_Findings_safety")
```

`r saf_conc1`

```{=tex}
}}
\ifdim\dimexpr\ht0+\dp0<7.0cm 
\dp0\dimexpr7.0cm-\ht0\fi

\fbox{\usebox{0}}
```

### Environment (SES RP3 area)

```{=tex}
\sbox{0}{\parbox{1\textwidth}{

\begin{wrapfigure}[13]{l}{0.5\linewidth}
\vspace{-15pt}

```

```{r chart-env-kea, options = (doclevel=c("level1"))}
#| file: R/chart_level1_kea.R
#| out.width: "100%"
```

```{=tex}
\end{wrapfigure}

\setlength\parskip{1em plus 0.8em} % Space between paragraphs
```

```{r}
env_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "environment", "Table_Findings_environment")
```

`r env_conc1`
```{=tex}
}}
\ifdim\dimexpr\ht0+\dp0<7.0cm 
\dp0\dimexpr7.0cm-\ht0\fi

\fbox{\usebox{0}}
```

### Capacity (SES RP3 area)

```{=tex}
\sbox{0}{\parbox{1\textwidth}{

\begin{wrapfigure}[26]{l}{0.5\linewidth}
\vspace{-15pt}

```

```{r chart-cap-er, options = (cztype=c("enroute"))}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

```{=tex}
\vspace{10pt} % vertical space between charts
```

```{r chart-cap-trm, options = (cztype=c("terminal"))}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

```{=tex}
\end{wrapfigure}

\setlength\parskip{1em plus 0.8em} % Space between paragraphs
```

```{r}
cap_er_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "ER_capacity", "Table_Findings_ER_capacity")
```

`r cap_er_conc1`
```{=tex}
}}
\ifdim\dimexpr\ht0+\dp0<7.0cm 
\dp0\dimexpr7.0cm-\ht0\fi

\fbox{\usebox{0}}
```

### Cost-efficiency (SES RP3 area)

```{=tex}
\sbox{0}{\parbox{1\textwidth}{

\begin{wrapfigure}[27]{l}{0.5\linewidth}
\vspace{-15pt}

```

```{r}
#| file: R/chart_level1_cef_er_ses.R
#| out.width: "100%"
```

```{=tex}
\vspace{10pt} % vertical space between charts
```

```{r chart-cef-trm-1, options = (cz=c("1", "terminal", "level1"))}
#| file: R/chart_level1_cef.R
#| out.width: "100%"
```

```{=tex}
\end{wrapfigure}

\setlength\parskip{1em plus 0.8em} % Space between paragraphs
```

```{r}
cef_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "cost-efficiency", "Table_Findings_CEFF")
```

`r cef_conc1`

```{=tex}
}}
\ifdim\dimexpr\ht0+\dp0<7.0cm 
\dp0\dimexpr7.0cm-\ht0\fi

\fbox{\usebox{0}}

\clearpage
```

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

## Safety - SES RP3

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

### PRB monitoring
```{r}
# saf_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "safety", "Table_Findings_safety")
```

`r saf_conc1`

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

### Actual versus planned number of ANSPs achieving the level of the EoSM targets for RP3 ahead of 2024

```{r chart-saf-ansp}
#| file: R/chart_level1_saf_ses.R
#| out.width: "52%"
#| fig.align: "center"
```

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

### Occurrences - Rate of runway incursions (RIs) (PI#1) & Rate of separation minima infringements (SMIs) (PI#2)

:::: {layout="[ 50, 50 ]"}

::::: {#chart-saf-ri}
```{r chart-saf-ri}
#| file: R/chart_level2_saf_ri.R
#| out.width: "100%"
```
:::::

::::: {#chart-saf-smi}
```{r chart-saf-smi}
#| file: R/chart_level2_saf_smi.R
#| out.width: "100%"
```
:::::

::::

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

## Environment - SES RP3

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

### PRB monitoring
```{r}
env_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "environment", "Table_Findings_environment")
```

`r env_conc1`

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

### En route performance

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

#### Horizontal flight efficiency of the actual trajectory (KEA) (KPI#1), of the last filed flight plan (KEP) (PI#1) & shortest constrained route (SCR) (PI#2)

:::: {layout="[ 50, 50 ]"}

::::: {#chart-env-kea}
```{r chart-env-kea-l2, options = (doclevel=c("level2"))}
#| file: R/chart_level1_kea.R
#| out.width: "100%"
```
:::::

::::: {#chart-env-kea-month}
```{r chart-env-kea-month}
#| file: R/chart_level2_kea_month.R
#| out.width: "100%"
```
:::::

::::

:::: {layout="[ 50, 50 ]"}

::::: {#chart-kep-scr}
```{r chart-env-kep-scr}
#| file: R/chart_level2_kep_scr.R
#| out.width: "100%"
```
:::::

::::: {#chart-kep-scr-month}
```{r chart-env-kep-scr-month}
#| file: R/chart_level2_kep_scr_month.R
#| out.width: "100%"
```
:::::

::::

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

#### Summary of performance at local level

:::: {layout="[ 10, 80, 10 ]"}

:::::{#empty-div}
```{=tex}
\hspace*{2cm}
```
:::::

::::: {#table-kea-summary}
```{r table-kea-summary}
#| file: R/table_env_kea_all_states.R
```

```{=tex}
```

`r table_env_kea_all_states`

```{=tex}
```
:::::

:::::{#empty-div}
```{=tex}
\hspace*{2cm}
```
:::::
::::

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

## Capacity - SES RP3

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

### PRB monitoring

```{r cap-prb}
  cap_er_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "ER_capacity", "Table_Findings_ER_capacity")
```

`r cap_er_conc1`

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

### En route performance

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

#### En route ATFM delay (KPI#1)

:::: {layout="[ 50, 50 ]"}
::::: {#chart-cap-er-l2}
```{r chart-cap-er-l2, options = (cztype=c("enroute"))}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```
:::::

::::: {#chart-cap-er-month}
```{r chart-cap-er-month, options = (cztype=c("enroute"))}
#| file: R/chart_level2_cap_month.R
#| out.width: "100%"
```
:::::
::::

```{r chart-cap-delay-bin}
#| file: R/chart_level2_cap_delay_bin.R
#| out.width: "52%"
#| fig.align: "center"
```


```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

#### Summary of performance at local level

:::: {layout="[ 10, 80, 10 ]"}

:::::{#empty-div}
```{=tex}
\hspace*{2cm}
```
:::::

::::: {#table-cap-erdelay-summary}
```{r table-cap-erdelay-summary}
#| file: R/table_cap_erdelay_all_states.R
```

```{=tex}
```

`r table_cap_erdelay_all_states`

```{=tex}
```
:::::

:::::{#empty-div}
```{=tex}
\hspace*{2cm}
```
:::::
::::


```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

#### Other indicators

:::: {layout="[ 50, 50 ]"}
::::: {#chart-cap-atco}
```{r chart-cap-atco}
#| file: R/chart_level2_cap_atco.R
#| out.width: "100%"
```
:::::

::::: {#chart-cap-er-month}
```{r chart-cap-sector-opening-ses}
#| file: R/chart_level2_cap_sector_opening.R
#| out.width: "100%"
```
:::::
::::

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

### Terminal performance

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

#### Arrival ATFM delay (KPI#2)

::::: {layout="[ 50, 50 ]"}

:::::: {#chart-cap-trm-l2}
```{r chart-cap-trm-l2, options = (cztype=c("terminal"))}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```
::::::

:::::: {#chart-cap-trm-month}
```{r chart-cap-trm-month, options = (cztype=c("terminal"))}
#| file: R/chart_level2_cap_month.R
#| out.width: "100%"
```
::::::
:::::

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

#### Summary of performance at local level

:::: {layout="[ 10, 80, 10 ]"}

:::::{#empty-div}
```{=tex}
\hspace*{2cm}
```
:::::

::::: {#table-cap-arrdelay-summary}
```{r table-cap-arrdelay-summary}
#| file: R/table_cap_arrdelay_all_states.R
```

```{=tex}
```

`r table_cap_arrdelay_all_states`

```{=tex}
```
:::::

:::::{#empty-div}
```{=tex}
\hspace*{2cm}
```
:::::
::::

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

#### Other terminal performance indicators (PI#1-3)

```{r chart-cap-all-causes-delay-ses}
#| file: R/chart_level2_cap_all_causes_delay.R
#| out.width: "52%"
#| fig.align: "center"
```

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

## Cost-efficiency - SES RP3

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

### PRB monitoring

:::: {#concl-cef-duc}
```{r concl-cef-duc}
cef_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "cost-efficiency", "Table_Findings_CEFF")
```
::::

`r cef_conc1`

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

### En route charging zone

:::: {layout="[ 50, 50 ]"}
::::: {#chart-cef-duc}
```{r chart-cef-duc-er-ses, options = (cz=c("1", "enroute"))}
#| file: R/chart_level1_cef_er_ses.R
#| out.width: "100%"
```
:::::

::::: {#chart-cef-su}
```{r chart-cef-su, options = (cz=c("1", "enroute"))}
#| file: R/chart_level2_cef_su.R
#| out.width: "100%"
```
:::::
::::

:::: {layout="[ 50, 1, 49 ]"}
::::: {#chart-cef-cost}
```{r chart-cef-cost, options = (cz=c("1", "enroute"))}
#| file: R/chart_level2_cef_cost.R
#| out.width: "100%"
```
:::::

:::::{#empty-div}
```{=tex}
\hspace*{0.1cm}
```
:::::

::::: {#table-costs}
```{r table-cef-cost, options = (cz=c("1", "enroute"))}
#| file: R/table_level2_cef_cost.R
```

```{=tex}
\vspace*{-3.8cm}
```

`r table_level2_cef_cost`

:::::
::::

:::: {layout="[ 50, 50 ]"}
::::: {#chart-cef-cost-entity}
```{r chart-cef-cost-entity, options = (cz=c("1", "enroute"))}
#| file: R/chart_level2_cef_cost_entity.R
#| out.width: "100%"
```
:::::

::::: {#chart-cef-cost-main}
```{r chart-cef-cost-main, options = (cz=c("1", "enroute"))}
#| file: R/chart_level2_cef_cost_main.R
#| out.width: "100%"
```
:::::
::::

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

#### Summary of performance at local level

:::: {#table-cef-summary}
```{r table-cef-summary, options = (cztype="enroute")}
#| file: R/table_cef_summary.R
#| out.width: "100%"
#| fig-asp: 1
```
::::

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
```

#### Actual unit cost incurred by the users (AUCU) (PI#1)

:::: {layout="[ 50, 2, 48 ]"}
::::: {#chart-cef-aucu}
```{r chart-cef-aucu, options = (cz=c("1", "enroute"))}
#| file: R/chart_level2_cef_aucu.R
#| out.width: "100%"
```
:::::

:::::{#empty-div}
```{=tex}
\hspace*{0.2cm}
```
:::::

::::: {#table-cef-aucu}
```{r table-cef-aucu, options = (cz=c("1", "enroute"))}
#| file: R/table_level2_cef_aucu.R
```

```{=tex}
\vspace*{-1.5cm}
```

`r table_level2_cef_aucu`

:::::
::::


:::: {layout="[ 50, 2, 48 ]"}
::::: {#chart-cef-er-cex}
```{r chart-cef-cex, R.options = (cz=c("1", "enroute"))}
#| file: R/chart_level2_cef_cex.R
#| out.width: "100%"
```
:::::

:::::{#empty-div}
```{=tex}
\hspace*{0.2cm}
```
:::::

::::: {#table-cef-er-cex}
```{r table-cef-cex, R.options = (cz=c("1", "enroute"))}
#| file: R/table_level2_cef_cex.R
```

```{=tex}
\vspace*{-2cm}
```

`r table_level2_cef_cex`

:::::
::::

#### Regulatory result (RR)

```{=tex}
\begin{figure}[H]
\begin{minipage}{0.50\linewidth}
```

```{r chart-cef-reg-res, options = (cz=c("1", "enroute"))}
#| file: R/chart_level2_cef_reg_res.R
#| out.width: "100%"
```

```{=tex}
\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
```

```{r chart-cef-reg-res_aucu,  options = (cz=c("1", "enroute"))}
#| file: R/chart_level2_cef_reg_res_aucu.R
#| out.width: "100%"
```

```{=tex}
\end{minipage}%
\end{figure}%
```

```{=tex}
\begin{figure}[H]
\begin{minipage}{0.50\linewidth}
```

```{r chart-cef-reg-res-ansp, options = (cz=c("1", "enroute"))}
#| file: R/chart_level2_cef_reg_res_ansp.R
#| out.width: "100%"
```

```{=tex}
\end{minipage}%
%
\begin{minipage}{0.50\linewidth}
```

```{r chart-cef-net-res-main-ansp, options = (cz=c("1", "enroute"))}
#| file: R/chart_level2_cef_net_res_main_ansp.R
#| out.width: "100%"
```

```{=tex}
\end{minipage}%
\end{figure}%
```

```{=tex}
\FloatBarrier % Prevent figures from moving beyond this point
\clearpage
\thispagestyle{empty} % Remove headers and footers from the final page
\begin{center}
\vspace*{\fill} % Center the text vertically
{\fontsize{20pt}{24pt}\selectfont \textbf{End of document}}
\vspace*{\fill}
\end{center}
```
