<!-- ### Traffic (SES RP3 area) L1 -->

```{r chart_level1_traffic_mvt, include=FALSE}
#| file: R/chart_level1_traffic_mvt.R
#| out.width: "100%"
```

```{r chart_level1_traffic_su, include=FALSE}
#| file: R/chart_level1_traffic_su.R
#| out.width: "100%"
```

<!-- ### Safety (SES RP3 area) L1 -->

```{r chart_level1_saf_ses, include=FALSE}
#| file: R/chart_level1_saf_ses.R
#| out.width: "100%"
```

<!-- ### Environment (SES RP3 area) L1 -->

```{r chart_env_kea, options = (doclevel=c("level1")), include=FALSE}
#| file: R/chart_level1_kea.R
#| out.width: "100%"
```
<!-- ### Capacity (SES RP3 area) L1 -->

```{r chart_cap_er, options = (cztype=c("enroute")), include=FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

```{r chart_cap_trm, options = (cztype=c("terminal")), include=FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

<!-- ### Cost-efficiency (SES RP3 area) L1-->

```{r chart_level1_cef_er_ses, include=FALSE}
#| file: R/chart_level1_cef_er_ses.R
#| out.width: "100%"
```

```{r chart_cef_trm_1, options = (cz=c("1", "terminal", "level1")), include=FALSE}
#| file: R/chart_level1_cef.R
#| out.width: "100%"
```

<!-- ### Occurrences - Rate of runway incursions (RIs) (PI#1) & Rate of separation minima infringements (SMIs) (PI#2) -->

```{r chart_saf_ri, include=FALSE}
#| file: R/chart_level2_saf_ri.R
#| out.width: "100%"
```

```{r chart_saf_smi, include=FALSE}
#| file: R/chart_level2_saf_smi.R
#| out.width: "100%"
```


<!-- ### En route performance -->
<!-- #### Horizontal flight efficiency of the actual trajectory (KEA) (KPI#1), of the last filed flight plan (KEP) (PI#1) & shortest constrained route (SCR) (PI#2) -->

```{r chart_env_kea_l2, options = (doclevel=c("level2")), include=FALSE}
#| file: R/chart_level1_kea.R
#| out.width: "100%"
```

```{r chart_env_kea_month, include=FALSE}
#| file: R/chart_level2_kea_month.R
#| out.width: "100%"
```

```{r chart_env_kep_scr, include=FALSE}
#| file: R/chart_level2_kep_scr.R
#| out.width: "100%"
```

```{r chart_env_kep_scr_month, include=FALSE}
#| file: R/chart_level2_kep_scr_month.R
#| out.width: "100%"
```


<!-- ### En route performance -->
<!-- #### En route ATFM delay (KPI#1) -->
```{r chart_cap_er_l2, options = (cztype=c("enroute")), include=FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

```{r chart_cap_er_month, options = (cztype=c("enroute")), include=FALSE}
#| file: R/chart_level2_cap_month.R
#| out.width: "100%"
```
<!-- #### Other indicators -->

```{r chart_cap_atco, include=FALSE}
#| file: R/chart_level2_cap_atco.R
#| out.width: "100%"
```

```{r chart_cap_sector_opening_ses, include=FALSE}
#| file: R/chart_level2_cap_sector_opening.R
#| out.width: "100%"
```

<!-- #### Arrival ATFM delay (KPI#2) -->
```{r chart_cap_trm_l2, options = (cztype=c("terminal")), include=FALSE}
#| file: R/chart_level1_cap.R
#| out.width: "100%"
```

```{r chart_cap_trm_month, options = (cztype=c("terminal")), include=FALSE}
#| file: R/chart_level2_cap_month.R
#| out.width: "100%"
```

<!-- En route charging zone -->
```{r chart_cef_duc_er_ses, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level1_cef_er_ses.R
#| out.width: "100%"
```

```{r chart_cef_su, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_su.R
#| out.width: "100%"
```

```{r chart_cef_cost, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_cost.R
#| out.width: "100%"
```

```{r table_cef_cost, options = (cz=c("1", "enroute"))}
mytable <-"table_level2_cef_cost"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

<!-- AUCU -->
```{r chart_cef_aucu, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_aucu.R
#| out.width: "100%"
```

```{r table_cef_aucu, options = (cz=c("1", "enroute"))}
mytable <-"table_level2_cef_aucu"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

```{r chart_cef_cex, R.options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_cex.R
#| out.width: "100%"
```

```{r table_cef_cex, R.options = (cz=c("1", "enroute"))}
mytable <-"table_level2_cef_cex"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

<!-- regulatory result -->
```{r chart_cef_reg_res, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_reg_res.R
#| out.width: "100%"
```

```{r chart_cef_reg_res_aucu,  options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_reg_res_aucu.R
#| out.width: "100%"
```

```{r chart_cef_reg_res_ansp, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_reg_res_ansp.R
#| out.width: "100%"
```

```{r chart_cef_net_res_main_ansp, options = (cz=c("1", "enroute")), include=FALSE}
#| file: R/chart_level2_cef_net_res_main_ansp.R
#| out.width: "100%"
```


# OVERVIEW

## Contextual information
```{r fetch-data-ses, eval=TRUE}
data_context <-read_xlsx(
  paste0(data_folder, "SES file.xlsx"),
  sheet = "Context",
  range = cell_limits(c(1, 1), c(NA, NA))) %>%
  as_tibble() %>% 
  clean_names() %>% 
  filter(year_report == .env$year_report & year == .env$year_report)

acc_no_context <- data_context %>% select(number_of_acc) %>% pull()
no_apt_big_context <- data_context %>% select(no_apts_big) %>% pull()
no_apt_small_context <- data_context %>% select(no_apts_small) %>% pull()

ert_trm_share_context <- data_context %>% select(ert_trm_share) %>% pull()
ert_cz_context <- data_context %>% select(ert_cz) %>% pull()
trm_cz_context <- data_context %>% select(trm_cz) %>% pull()

main_ansp_context <- data_context %>% select(main_ans_ps_ert) %>% pull()
other_ansp_context <- data_context %>% select(other_ans_ps_ert) %>% pull()
met_ansp_context <- data_context %>% select(met_providers) %>% pull()
```

::: {layout="[ 34, 38, 28 ]"}

::::{#1st-column}
**No of ACCs   ** `r acc_no_context`  
```{=tex}
\par\vspace{1em}
```

**No of airports in the scope**
```{=tex}
```
**of the performance plan:**

- **≥80'K     ** `r no_apt_big_context`
- **<80'K     ** `r no_apt_small_context`

::::

::::{#2nd-column}
```{=tex}
\vspace*{-\baselineskip} % Adjust vertical alignment to the top
```
**Share en route / terminal**
```{=tex}
```
**costs `r year_report`                 ** `r ert_trm_share_context`
```{=tex}
\par\vspace{1em}
```
**En route charging zone(s)     ** `r ert_cz_context`
```{=tex}
\par\vspace{1em}
```
**Terminal charging zone(s)    ** `r trm_cz_context`
::::

::::{#3rd-column}
```{=tex}
\vspace*{-\baselineskip} % Adjust vertical alignment to the top
\vspace{-1.5em}
```
**No of main ANSPs     ** `r main_ansp_context`
```{=tex}
\par\vspace{1em}
```
**No of other ANSPs    ** `r other_ansp_context`
```{=tex}
\par\vspace{1em}
```
**No of MET Providers ** `r met_ansp_context`
::::

:::


## Main PRB findings - {{< var doc.year_report >}}

```{r main-concl}
main_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "main", "Table_Findings_main")
```

`r main_conc1`


## Traffic (SES RP3 area)
```{=tex}
\setlength{\fboxrule}{0pt} % Set the border width to 0pt (no border)
\setlength{\fboxsep}{0pt} % Remove padding
```

```{r mvt_conc1}
mvt_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "traffic_IFR", "Table_Findings_traffic_IFR")
mvt_text <- break_l1_text(mvt_conc1) 
mvt_text1 <- mvt_text$text1
mvt_text2 <- mvt_text$text2
```

`r paste0(layout_wrap_figure("chart_level1_traffic_mvt", NULL, mvt_text1, 12), mvt_text2)`

```{r su_conc1}
tsu_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "traffic_SUs", "Table_Findings_traffic_TSU")
tsu_text <- break_l1_text(tsu_conc1) 
tsu_text1 <- tsu_text$text1
tsu_text2 <- tsu_text$text2
```

`r paste0(layout_wrap_figure("chart_level1_traffic_su", NULL, tsu_text1, 12), tsu_text2)`

## Safety (SES RP3 area)

```{r saf_conc1}
saf_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "safety", "Table_Findings_safety")
saf_text_conc <- break_l1_text(saf_conc1) 
saf_text1 <- saf_text_conc$text1
saf_text2 <- saf_text_conc$text2
```

`r paste0(layout_wrap_figure("chart_level1_saf_ses", NULL, saf_text1, 13), saf_text2)`

## Environment (SES RP3 area)

```{r env_conc1}
env_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "environment", "Table_Findings_environment")
env_text <- break_l1_text(env_conc1) 
env_text1 <- env_text$text1
env_text2 <- env_text$text2
```

`r paste0(layout_wrap_figure("chart_env_kea", NULL, env_text1, 13), env_text2)`

## Capacity (SES RP3 area)

```{r cap_er_conc1}
cap_er_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "ER_capacity", "Table_Findings_ER_capacity")
```

`r layout_wrap_figure("chart_cap_er", "chart_cap_trm", cap_er_conc1, 25, boxsize = 13.5)`


## Cost-efficiency (SES RP3 area)

```{r cef_conc_l1}
cef_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "cost-efficiency", "Table_Findings_CEFF")
```

`r layout_wrap_figure("chart_level1_cef_er_ses", "chart_cef_trm_1", cef_conc1, 25, boxsize = 13.5)`

\needspace{3\baselineskip}

# SAFETY - SES RP3

## PRB monitoring
```{r}
# saf_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "safety", "Table_Findings_safety")
```

`r saf_conc1`

## Actual versus planned number of ANSPs achieving the level of the EoSM targets for RP3 ahead of 2024

```{r chart_saf_ansp}
#| file: R/chart_level1_saf_ses.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

## Occurrences - Rate of runway incursions (RIs) (PI#1) & Rate of separation minima infringements (SMIs) (PI#2)

`r layout_2fig("chart_saf_ri", "chart_saf_smi")`


\needspace{3\baselineskip}

# ENVIRONMENT - SES RP3

## PRB monitoring
```{r}
env_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "environment", "Table_Findings_environment")
```

`r env_conc1`

\needspace{3\baselineskip}

## En route performance

### Horizontal flight efficiency of the actual trajectory (KEA) (KPI#1), of the last filed flight plan (KEP) (PI#1) & shortest constrained route (SCR) (PI#2)

`r layout_2fig("chart_env_kea_l2", "chart_env_kea_month")`

`r layout_2fig("chart_env_kep_scr", "chart_env_kep_scr_month")`

### Summary of performance at local level

```{r table_kea_summary}
mytable <-"table_env_kea_all_states"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

`r layout_summary_table(table_env_kea_all_states, left_margin = 1.7)`


\needspace{3\baselineskip}

# CAPACITY - SES RP3

## PRB monitoring

```{r cap_prb}
  cap_er_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "ER_capacity", "Table_Findings_ER_capacity")
```

`r cap_er_conc1`

\needspace{3\baselineskip}

## En route performance

### En route ATFM delay (KPI#1)

`r layout_2fig("chart_cap_er_l2", "chart_cap_er_month")`

```{r chart_cap_delay_bin}
#| file: R/chart_level2_cap_delay_bin.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

### Summary of performance at local level

```{r table_cap_erdelay_summary}
mytable <-"table_cap_erdelay_all_states"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

`r layout_summary_table(table_cap_erdelay_all_states, left_margin = 1.7)`

### Other indicators

`r layout_2fig("chart_cap_atco", "chart_cap_sector_opening_ses")`


\needspace{3\baselineskip}

## Terminal performance

### Arrival ATFM delay (KPI#2)

`r layout_2fig("chart_cap_trm_l2", "chart_cap_trm_month")`

### Summary of performance at local level

```{r table_cap_arrdelay_summary}
mytable <-"table_cap_arrdelay_all_states"
table_string <- source(here("R", paste0(mytable,".R"))) 
assign(mytable, setup_latex_table(get(mytable))) 
```

`r layout_summary_table(table_cap_arrdelay_all_states, left_margin = 1.7)`

### Other terminal performance indicators (PI#1-3)

```{r chart_cap_all_causes_delay_ses}
#| file: R/chart_level2_cap_all_causes_delay.R
#| out.width: "52%"
#| fig.align: "center"
#| fig-pos: "H"
```

\needspace{3\baselineskip}

# COST-EFFICIENCY - SES RP3

## PRB monitoring

:::: {#concl-cef-duc}
```{r concl_cef_duc}
cef_conc1 <- get_prb_conclusions("PRB_findings.xlsx", "cost-efficiency", "Table_Findings_CEFF")
```
::::

`r cef_conc1`


## En route charging zone

`r layout_2fig("chart_cef_duc_er_ses", "chart_cef_su")`

`r layout_fig_table("chart_cef_cost", table_level2_cef_cost, vspace = -3.8)`

### Summary of performance at local level

:::: {#table-cef-summary}
```{r table_cef_summary, options = (cztype="enroute")}
#| file: R/table_cef_summary.R
#| out.width: "100%"
#| fig-asp: 1
```
::::

### Actual unit cost incurred by the users (AUCU) (PI#1)

`r layout_fig_table("chart_cef_aucu", table_level2_cef_aucu, vspace = -1.5)`

`r layout_fig_table("chart_cef_cex", table_level2_cef_cex, vspace = -2)`

### Regulatory result (RR)

`r layout_2fig("chart_cef_reg_res", "chart_cef_reg_res_aucu")`

`r layout_2fig("chart_cef_reg_res_ansp", "chart_cef_net_res_main_ansp")`

